### 2015-08-21 templates/report/research/tex/academic_works.tex
Testing tex file

{% block content %}

{% if postdoc_concluded or postdoc_in_progress or phd_concluded or phd_in_progress or msc_concluded or msc_in_progress %}
	{% if postdoc_concluded or postdoc_in_progress %}
\subsubsection{Post-doctoral fellows}
		{% if postdoc_concluded %}
\paragraph{Concluded}
\begin{enumerate}
			{% for postdoc in postdoc_concluded %}
	\item Title of the project: {{ postdoc.title }}
	\begin{itemize}
		\item Period: {{ postdoc.start_date }} to {{ postdoc.end_date }}
		\item Name of the student: {{ postdoc.advisee }}
		\item Advisor: {{ postdoc.advisor }}
		{% if postdoc.co_advisors %}\item Co-advisor: {{ postdoc.co_advisors }}{% endif %}
		\item Institution: {{ postdoc.institution }}
		{% if postdoc.schollarship %}\item Schollarship: {{ postdoc.schollarship }}{% endif %}
	\end{itemize}
             {% endfor %}
\end{enumerate}
		{% endif %}	
	{% endif %}
{%  else %}
    No academic works found!
{% endif %}

{% endblock %}

### 2015-08-26 research/views.py
academic works was divided into two views, one to generate the html and another to generate the tex file. The output is ok.

@@ -38,7 +38,6 @@ def now_plus_five_years():
 
 @login_required
 def articles(request):
-
     if request.method == 'POST':
         start_date = request.POST['start_date']
         if start_date:
@@ -96,40 +95,31 @@ def articles(request):
     return render(request, 'report/research/articles.html')
 
 
+def search_academic_works(start_date, end_date):
+    # Get all the Postdocs among the chosen dates
+    postdoc_concluded = AcademicWork.objects.filter(type__name='Post-doctoral', status='c', end_date__gt=start_date,
+                                                    end_date__lt=end_date).order_by('-end_date')
+    postdoc_in_progress = AcademicWork.objects.filter(type__name='Post-doctoral', status='i',
+                                                      start_date__lt=end_date).order_by('-end_date')
+
+    # Get all the PhDs among the chosen dates
+    phd_concluded = AcademicWork.objects.filter(type__name='PhD', status='c', end_date__gt=start_date,
+                                                end_date__lt=end_date).order_by('-end_date')
+    phd_in_progress = AcademicWork.objects.filter(type__name='PhD', status='i',
+                                                  start_date__lt=end_date).order_by('-end_date')
+
+    # Get all the MScs among the chosen dates
+    msc_concluded = AcademicWork.objects.filter(type__name='MSc', status='c', end_date__gt=start_date,
+                                                end_date__lt=end_date).order_by('-end_date')
+    msc_in_progress = AcademicWork.objects.filter(type__name='MSc', status='i',
+                                                  start_date__lt=end_date).order_by('-end_date')
+
+    return postdoc_concluded, postdoc_in_progress, phd_concluded, phd_in_progress, msc_concluded, msc_in_progress
+
+
 @login_required
-def academic_works(request, tex=False):
-
-    if tex:
-        start_date = request.GET.get('start_date')
-        end_date = request.GET.get('end_date')
-
-        # Get all the Postdocs among the chosen dates
-        postdoc_concluded = AcademicWork.objects.filter(type__name='Post-doctoral', status='c', end_date__gt=start_date,
-                                                        end_date__lt=end_date).order_by('-end_date')
-        postdoc_in_progress = AcademicWork.objects.filter(type__name='Post-doctoral', status='i',
-                                                          start_date__lt=end_date).order_by('-end_date')
-
-        # Get all the PhDs among the chosen dates
-        phd_concluded = AcademicWork.objects.filter(type__name='PhD', status='c', end_date__gt=start_date,
[…]

### 2015-08-26 research/urls.py
New url to create the tex file

@@ -5,5 +5,5 @@ from research import views
 urlpatterns = patterns('',
     url(r'^articles/$', views.articles, name='articles'),
     url(r'^academic_works/$', views.academic_works, name='academic_works'),
-    url(r'^academic_works/(?P<tex>\d)$', views.academic_works, name='academic_works'),
+    url(r'^academic_works_tex/$', views.academic_works_tex, name='academic_works_tex'),
 )

### 2015-08-26 research/admin.py
Removed status from AcademicWorks

@@ -76,9 +76,9 @@ admin.site.register(Event, EventAdmin)
 
 
 class AcademicWorkAdmin(admin.ModelAdmin):
-    fields = ['type', 'status', 'title', 'advisee', 'advisor', 'co_advisor', 'institution', 'schollarship',
-              'start_date', 'end_date']
-    list_display = ('title', 'advisee', 'advisor', 'type', 'status', 'start_date', 'end_date')
+    fields = ['type', 'title', 'advisee', 'advisor', 'co_advisor', 'institution', 'schollarship', 'start_date',
+              'end_date']
+    list_display = ('title', 'advisee', 'advisor', 'type', 'start_date', 'end_date')
     list_display_links = ('title',)
 
     # Shows the academic work according to the user permission

### 2015-08-26 research/models.py

@@ -279,10 +279,9 @@ class AcademicWork(models.Model):
     co_advisor = models.ManyToManyField(Person, verbose_name=_('Co-Advisor'),
                                         related_name='co_advisor_academic_work', blank=True, null=True)
     institution = models.ForeignKey(Institution, verbose_name=_('Institution'))
-    status = models.CharField(_('Status'), max_length=1, choices=STATUS_ANSWER)
     schollarship = models.CharField(_('Schollarship'), max_length=255, blank=True, null=True)
     start_date = models.DateField(_('Start date'))
-    end_date = models.DateField(_('End date'))
+    end_date = models.DateField(_('End date'), blank=True, null=True)
 
     def __unicode__(self):
         return u'%s' % self.title
@@ -293,4 +292,4 @@ class AcademicWork(models.Model):
     class Meta:
         verbose_name = _('Academic Work')
         verbose_name_plural = _('Academic Works')
-        ordering = ('-end_date', )
+        ordering = ('-start_date', )

### 2015-08-26 research/views.py
Removed status from search_academic_works. Check if end_date is null in all _in_progress

@@ -97,22 +97,22 @@ def articles(request):
 
 def search_academic_works(start_date, end_date):
     # Get all the Postdocs among the chosen dates
-    postdoc_concluded = AcademicWork.objects.filter(type__name='Post-doctoral', status='c', end_date__gt=start_date,
+    postdoc_concluded = AcademicWork.objects.filter(type__name='Post-doctoral', end_date__gt=start_date,
                                                     end_date__lt=end_date).order_by('-end_date')
-    postdoc_in_progress = AcademicWork.objects.filter(type__name='Post-doctoral', status='i',
-                                                      start_date__lt=end_date).order_by('-end_date')
+    postdoc_in_progress = AcademicWork.objects.filter(type__name='Post-doctoral', start_date__lt=end_date,
+                                                      end_date__isnull=True).order_by('-start_date')
 
     # Get all the PhDs among the chosen dates
-    phd_concluded = AcademicWork.objects.filter(type__name='PhD', status='c', end_date__gt=start_date,
+    phd_concluded = AcademicWork.objects.filter(type__name='PhD', end_date__gt=start_date,
                                                 end_date__lt=end_date).order_by('-end_date')
-    phd_in_progress = AcademicWork.objects.filter(type__name='PhD', status='i',
-                                                  start_date__lt=end_date).order_by('-end_date')
+    phd_in_progress = AcademicWork.objects.filter(type__name='PhD', start_date__lt=end_date,
+                                                  end_date__isnull=True).order_by('-start_date')
 
     # Get all the MScs among the chosen dates
-    msc_concluded = AcademicWork.objects.filter(type__name='MSc', status='c', end_date__gt=start_date,
+    msc_concluded = AcademicWork.objects.filter(type__name='MSc', end_date__gt=start_date,
                                                 end_date__lt=end_date).order_by('-end_date')
-    msc_in_progress = AcademicWork.objects.filter(type__name='MSc', status='i',
-                                                  start_date__lt=end_date).order_by('-end_date')
+    msc_in_progress = AcademicWork.objects.filter(type__name='MSc', start_date__lt=end_date,
+                                                  end_date__isnull=True).order_by('-start_date')
 
     return postdoc_concluded, postdoc_in_progress, phd_concluded, phd_in_progress, msc_concluded, msc_in_progress
 

### 2015-08-27 research/views.py
Bug fix. The report correctly returns even using old dates.

@@ -5,6 +5,7 @@ from django.contrib import messages
 from models import ResearchResult, AcademicWork
 import datetime
 from django.template.loader import render_to_string
+from django.db.models import Q
 
 TIME = " 00:00:00"
 
@@ -99,20 +100,21 @@ def search_academic_works(start_date, end_date):
     # Get all the Postdocs among the chosen dates
     postdoc_concluded = AcademicWork.objects.filter(type__name='Post-doctoral', end_date__gt=start_date,
                                                     end_date__lt=end_date).order_by('-end_date')
-    postdoc_in_progress = AcademicWork.objects.filter(type__name='Post-doctoral', start_date__lt=end_date,
-                                                      end_date__isnull=True).order_by('-start_date')
+    postdoc_in_progress = AcademicWork.objects.filter(Q(end_date__isnull=True) | Q(end_date__gt=end_date),
+                                                      type__name='Post-doctoral',
+                                                      start_date__lt=end_date).order_by('-start_date')
 
     # Get all the PhDs among the chosen dates
     phd_concluded = AcademicWork.objects.filter(type__name='PhD', end_date__gt=start_date,
                                                 end_date__lt=end_date).order_by('-end_date')
-    phd_in_progress = AcademicWork.objects.filter(type__name='PhD', start_date__lt=end_date,
-                                                  end_date__isnull=True).order_by('-start_date')
+    phd_in_progress = AcademicWork.objects.filter(Q(end_date__isnull=True) | Q(end_date__gt=end_date),
+                                                  type__name='PhD', start_date__lt=end_date).order_by('-start_date')
 
     # Get all the MScs among the chosen dates
     msc_concluded = AcademicWork.objects.filter(type__name='MSc', end_date__gt=start_date,
                                                 end_date__lt=end_date).order_by('-end_date')
-    msc_in_progress = AcademicWork.objects.filter(type__name='MSc', start_date__lt=end_date,
-                                                  end_date__isnull=True).order_by('-start_date')
+    msc_in_progress = AcademicWork.objects.filter(Q(end_date__isnull=True) | Q(end_date__gt=end_date),
+                                                  type__name='MSc', start_date__lt=end_date).order_by('-start_date')
 
     return postdoc_concluded, postdoc_in_progress, phd_concluded, phd_in_progress, msc_concluded, msc_in_progress
 

### 2015-08-27 templates/report/research/tex/academic_works.tex
Latex template completed

@@
 {% block content %}
-
 {% if postdoc_concluded or postdoc_in_progress or phd_concluded or phd_in_progress or msc_concluded or msc_in_progress %}
@@
 \begin{enumerate}
-			{% for postdoc in postdoc_concluded %}
-	\item Title of the project: {{ postdoc.title }}
+			{% for result in postdoc_concluded %}
+	\item Title of the project: {{ result.title }}
 	\begin{itemize}
-		\item Period: {{ postdoc.start_date }} to {{ postdoc.end_date }}
-		\item Name of the student: {{ postdoc.advisee }}
-		\item Advisor: {{ postdoc.advisor }}
-		{% if postdoc.co_advisors %}\item Co-advisor: {{ postdoc.co_advisors }}{% endif %}
-		\item Institution: {{ postdoc.institution }}
-		{% if postdoc.schollarship %}\item Schollarship: {{ postdoc.schollarship }}{% endif %}
+		\item Period: {{ result.start_date }} to {{ result.end_date }}
+		\item Advisee: {{ result.advisee }}
+		\item Advisor: {{ result.advisor }}
+		{% if result.co_advisors %}\item Co-advisor: {{ result.co_advisors }}{% endif %}
+		\item Institution: {{ result.institution }}
+		{% if result.schollarship %}\item Schollarship: {{ result.schollarship }}{% endif %}
+	\end{itemize}
+             {% endfor %}
+\end{enumerate}
+		{% endif %}	
+		{% if postdoc_in_progress %}
+\paragraph{In progress}
+\begin{enumerate}
+			{% for result in postdoc_in_progress %}
+	\item Title of the project: {{ result.title }}
+	\begin{itemize}
+		\item Period: {{ result.start_date }} - ongoing
+		\item Advisee: {{ result.advisee }}
+		\item Advisor: {{ result.advisor }}
+		{% if result.co_advisors %}\item Co-advisor: {{ result.co_advisors }}{% endif %}
+		\item Institution: {{ result.institution }}
+		{% if result.schollarship %}\item Schollarship: {{ result.schollarship }}{% endif %}
 	\end{itemize}
@@
 	{% endif %}
+
+{% if phd_concluded or phd_in_progress %}
+\subsubsection{PhD thesis}
+		{% if phd_concluded %}
+\paragraph{Concluded}
+\begin{enumerate}
+			{% for result in phd_concluded %}
+	\item Title of the project: {{ result.title }}
+	\begin{itemize}
+		\item Period: {{ result.start_date }} to {{ result.end_date }}
+		\item Advisee: {{ result.advisee }}
+		\item Advisor: {{ result.advisor }}
+		{% if result.co_advisors %}\item Co-advisor: {{ result.co_advisors }}{% endif %}
+		\item Institution: {{ result.institution }}
+		{% if result.schollarship %}\item Schollarship: {{ result.schollarship }}{% endif %}
+	\end{itemize}
+             {% endfor %}
+\end{enumerate}
+		{% endif %}	
+		{% if phd_in_progress %}
+\paragraph{In progress}
+\begin{enumerate}
+			{% for result in phd_in_progress %}
+	\item Title of the project: {{ result.title }}
+	\begin{itemize}
+		\item Period: {{ result.start_date }} - ongoing
+		\item Advisee: {{ result.advisee }}
+		\item Advisor: {{ result.advisor }}
+		{% if result.co_advisors %}\item Co-advisor: {{ result.co_advisors }}{% endif %}
+		\item Institution: {{ result.institution }}
+		{% if result.schollarship %}\item Schollarship: {{ result.schollarship }}{% endif %}
+	\end{itemize}
+             {% endfor %}
+\end{enumerate}
+		{% endif %}	
+	{% endif %}
+
+{% if msc_concluded or msc_in_progress %}
+\subsubsection{MSc dissertations}
+		{% if msc_concluded %}
+\paragraph{Concluded}
+\begin{enumerate}
+			{% for result in msc_concluded %}
+	\item Title of the project: {{ result.title }}
+	\begin{itemize}
+		\item Period: {{ result.start_date }} to {{ result.end_date }}
+		\item Advisee: {{ result.advisee }}
+		\item Advisor: {{ result.advisor }}
+		{% if result.co_advisors %}\item Co-advisor: {{ result.co_advisors }}{% endif %}
+		\item Institution: {{ result.institution }}
+		{% if result.schollarship %}\item Schollarship: {{ result.schollarship }}{% endif %}
+	\end{itemize}
+             {% endfor %}
+\end{enumerate}
+		{% endif %}	
+		{% if msc_in_progress %}
+\paragraph{In progress}
+\begin{enumerate}
+			{% for result in msc_in_progress %}
+	\item Title of the project: {{ result.title }}
+	\begin{itemize}
+		\item Period: {{ result.start_date }} - ongoing
+		\item Advisee: {{ result.advisee }}
+		\item Advisor: {{ result.advisor }}
+		{% if result.co_advisors %}\item Co-advisor: {{ result.co_advisors }}{% endif %}
+		\item Institution: {{ result.institution }}
+		{% if result.schollarship %}\item Schollarship: {{ result.schollarship }}{% endif %}
+	\end{itemize}
+             {% endfor %}
+\end{enumerate}
+		{% endif %}	
+	{% endif %}
+
 {%  else %}
@@
 {% endif %}
-
 {% endblock %}

### 2015-08-27 research/admin.py
Institution removed. It will be used the institution from the advisee.

@@ -76,8 +76,7 @@ admin.site.register(Event, EventAdmin)
 
 
 class AcademicWorkAdmin(admin.ModelAdmin):
-    fields = ['type', 'title', 'advisee', 'advisor', 'co_advisor', 'institution', 'schollarship', 'start_date',
-              'end_date']
+    fields = ['type', 'title', 'advisee', 'advisor', 'co_advisor', 'schollarship', 'start_date', 'end_date']
     list_display = ('title', 'advisee', 'advisor', 'type', 'start_date', 'end_date')
     list_display_links = ('title',)
 

### 2015-08-27 research/models.py

@@ -276,9 +276,8 @@ class AcademicWork(models.Model):
     title = models.CharField(_('Title'), max_length=255)
     advisee = models.ForeignKey(Person, verbose_name=_('Advisee'))
     advisor = models.ForeignKey(Person, verbose_name=_('Advisor'), related_name='advisor_academic_work')
-    co_advisor = models.ManyToManyField(Person, verbose_name=_('Co-Advisor'),
-                                        related_name='co_advisor_academic_work', blank=True, null=True)
-    institution = models.ForeignKey(Institution, verbose_name=_('Institution'))
+    co_advisor = models.ManyToManyField(Person, verbose_name=_('Co-Advisor'), related_name='co_advisor_academic_work',
+                                        blank=True, null=True)
     schollarship = models.CharField(_('Schollarship'), max_length=255, blank=True, null=True)
     start_date = models.DateField(_('Start date'))
     end_date = models.DateField(_('End date'), blank=True, null=True)

### 2016-03-31 research/tests.py
NIRA-66 - Update the unit tests for Research app Writing tests for the Articles model.

@@ -2,13 +2,24 @@ from custom_auth.models import User
 from django.core.urlresolvers import reverse
 from django.test import TestCase
 from django.test.client import RequestFactory
+from django.utils.translation import ugettext_lazy as _
 from models import AcademicWork, TypeAcademicWork, Person, Article, Draft, Submitted, Accepted, PublishedInPeriodical, Periodical
 from views import scholar, scholar_info, valid_date, now_plus_five_years
+
 import datetime
+
 
 
 USERNAME = 'myuser'
 PASSWORD = 'mypassword'
+
+PERIODICAL = 'p'
+EVENT = 'e'
+
+ARTICLE_TYPE = (
+    (PERIODICAL, _('Periodical (Journal or magazine)')),
+    (EVENT, _('Event (Conference, congress, meeting, etc)')),
+)
 
 # DRY way for testing
 def createPostdoc(type, title, advisee, advisor, start_date, end_date):
@@ -364,7 +375,6 @@ class ScholarTest(TestCase):
             else:
                 ret = False
 
-        self.valid_scholar_list.extend(scholar_list)
         self.assertTrue(ret)
 
 
@@ -405,7 +415,6 @@ class DateTest(TestCase):
         """
         Test if helper method works
         """
-
         date = datetime.datetime.now() + datetime.timedelta(days=5*365)
         date = date.strftime("%Y%m%d %H:%M:%S")
         date = datetime.datetime.strptime(date, '%Y%m%d %H:%M:%S').date()
@@ -421,14 +430,27 @@ class ArticlesTest(TestCase):
     def setUp(self):
         title = "Test article"
         team = "Test team"
-        self.published = Article(title=title, team=team, status='Published')
-        self.accepted = Article(title=title, team=team, status='Accepted')
-        self.submitted = Article(title=title, team=team, status='Submitted')
-        self.draft = Article(title=title, team=team, status='Draft')
+        # Is this kind of creation correct?
+        self.published = Article(title=title, team=team, status=u'p')
+        self.accepted = Article(title=title, team=team, status=u'a')
+        self.submitted = Article(title=title, team=team, status=u's')
+        self.draft = Article(title=title, team=team, status=u'd')
+        self.periodical = Article(title=title, team=team, status=u'p', type='p')
+        self.event = Article(title=title, team=team, status=u'p', type='e')
+        self.factory = RequestFactory()
 
-    def current_status_test(self):
-        self.assertEqual('Published',self.published.current_status())
-        self.assertEqual('Accepted',self.accepted.current_status())
[…]

### 2016-03-31 research/views.py
Check if file that will be uploaded ends with .ris

@@ -325,7 +325,7 @@ def import_papers(request):
     """
 
     if request.method == 'POST':
-        if request.FILES:
+        if request.FILES and request.FILES['file'].name.endswith('.ris'):
             file_uploaded = request.FILES['file'].read().splitlines()
             paper = {}
             papers = []
@@ -370,7 +370,7 @@ def import_papers(request):
             return render(request, 'report/research/periodicals_to_import.html', context)
 
         else:
-            messages.warning(request, _("You didn't choose a file. Nothing to be done!"))
+            messages.warning(request, _("Please, select a .ris file to upload."))
 
     return render(request, 'report/research/import.html')
 

### 2016-03-31 research/views.py
PEP8 - messages removed

@@ -196,7 +196,7 @@ def academic_works(request):
             end_date = now_plus_five_years()
 
         postdoc_concluded, postdoc_in_progress, phd_concluded, phd_in_progress, msc_concluded, \
-        msc_in_progress = search_academic_works(start_date, end_date)
+            msc_in_progress = search_academic_works(start_date, end_date)
 
         if end_date >= start_date:
             context = {'postdoc_concluded': postdoc_concluded, 'postdoc_in_progress': postdoc_in_progress,
@@ -218,7 +218,7 @@ def academic_works_tex(request):
     end_date = request.GET.get('end_date')
 
     postdoc_concluded, postdoc_in_progress, phd_concluded, phd_in_progress, msc_concluded, \
-    msc_in_progress = search_academic_works(start_date, end_date)
+        msc_in_progress = search_academic_works(start_date, end_date)
 
     context = {'postdoc_concluded': postdoc_concluded, 'postdoc_in_progress': postdoc_in_progress,
                'phd_concluded': phd_concluded, 'phd_in_progress': phd_in_progress,

### 2016-03-31 research/tests.py
NIRA-66 - Update the unit tests for Research app

@@ -6,6 +6,7 @@ from models import AcademicWork, TypeAcademicWork, Person, Article, Draft, Submi
     Periodical
 from views import scholar, scholar_info, valid_date, now_plus_five_years
 import datetime
+from django.core.files.uploadedfile import SimpleUploadedFile
 
 
 USERNAME = 'myuser'
@@ -13,6 +14,17 @@ PASSWORD = 'mypassword'
 
 
 # DRY way for testing
+def system_authentication(instance):
+    user = User.objects.create_user(username=USERNAME, password=PASSWORD)
+    user.is_active = True
+    user.is_staff = True
+    user.is_superuser = True
+    user.save()
+    factory = RequestFactory()
+    logged = instance.client.login(username=USERNAME, password=PASSWORD)
+    return logged, user, factory
+
+
 def create_postdoc(type, title, advisee, advisor, start_date, end_date):
     postdoc = AcademicWork()
     postdoc.type = type
@@ -115,15 +127,7 @@ class ResearchTimelineTest(TestCase):
     published_07 = None
 
     def setUp(self):
-        self.user = User.objects.create_user(username=USERNAME, password=PASSWORD)
-        self.user.is_active = True
-        self.user.is_staff = True
-        self.user.is_superuser = True
-        self.user.save()
-
-        self.factory = RequestFactory()
-
-        logged = self.client.login(username=USERNAME, password=PASSWORD)
+        logged, self.user, self.factory = system_authentication(self)
         self.assertEqual(logged, True)
 
         academic_work = TypeAcademicWork.objects.create(name='Post-doctoral')
@@ -431,3 +435,22 @@ class ArticlesTest(TestCase):
         self.assertEqual('Submitted', self.submitted.current_status())
         self.assertEqual('Draft', self.draft.current_status())
         self.assertNotEqual('Published', self.accepted.current_status())
+
+
+class ImportPaper(TestCase):
+
+    def setUp(self):
+        logged, self.user, self.factory = system_authentication(self)
+        self.assertEqual(logged, True)
+
+    def test_import_file(self):
+        response = self.client.get(reverse('import_papers'))
+        self.assertEqual(response.status_code, 200)
+
+        ris_file = SimpleUploadedFile('citations.ris', b'rb')
+        response = self.client.post(reverse('import_papers'), {'file': ris_file})
+        self.assertEqual(response.status_code, 200)
+
[…]

### 2016-04-01 templates/report/research/tex/articles.tex
NIRA-60 - Create an article report in Latex format

{% block content %}

{% if published_scientific or accepted_scientific or submitted_scientific or draft_scientific or published_dissemin or accepted_dissemin or submitted_dissemin or draft_dissemin or published_tec_trans or accepted_tec_trans or submitted_tec_trans or draft_tec_trans or published_scientific_in_event or accepted_scientific_in_event or published_dissemin_in_event or accepted_dissemin_in_event or published_tec_trans_in_event or accepted_tec_trans_in_event%}

	{% if published_scientific or accepted_scientific %}
\subsubsection{Published or accepted}
		{% if published_scientific %}
\begin{enumerate}
			{% for article in published_scientific %}
				{% if not article.article.hide %} \item {% if article.article.url %} \textbf{ \href{ {{ article.article.url }} }{ {{ article.article.title }}. } }{% else %}{{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors  %} \textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %} {{ article.article.authors }} {{ article.article.periodical }},{% endif %}{% if article.volume %} \textbf{ {{ article.volume }} }{% endif %}{% if article.number %} ({{ article.number }}),{% endif %}{% if article.start_page and article.end_page %} {{ article.start_page }}-{{ article.end_page }},{% endif %} {% if article.doi %}DOI: {{ article.doi }},{% endif %} {{ article.date|date:"Y" }}.{% endif %}
			{% endfor %}
\end{enumerate}
		{% endif %}
	{% endif %}

{%  else %}
   	No articles found!
{% endif %}

{% endblock %}

### 2016-04-01 research/urls.py

@@ -4,6 +4,7 @@ from research import views
 
 urlpatterns = patterns('',
     url(r'^articles/$', views.articles, name='articles'),
+    url(r'^articles_tex/$', views.articles_tex, name='articles_tex'),
     url(r'^academic_works/$', views.academic_works, name='academic_works'),
     url(r'^academic_works_tex/$', views.academic_works_tex, name='academic_works_tex'),
     url(r'^import_papers/$', views.import_papers, name='import_papers'),

### 2016-04-01 research/views.py

@@ -61,6 +61,64 @@ def now_plus_five_years():
     return date
 
 
+def search_articles(start_date, end_date):
+    # List of articles
+    published_periodical = PublishedInPeriodical.objects.filter(article__type='p', date__gt=start_date,
+                                                                date__lt=end_date).order_by('date')
+    published_event = Published.objects.filter(article__type='e', article__event__start_date__lt=end_date,
+                                               article__event__end_date__gt=start_date).order_by('article__event__start_date')
+    accepted = Accepted.objects.filter(date__lt=end_date).order_by('date')
+    submitted = Submitted.objects.filter(date__lt=end_date).order_by('article_id').distinct('article_id')
+    draft = Draft.objects.filter(date__lt=end_date).order_by('article_id').distinct('article_id')
+
+    # Articles IDs
+    published_periodical_ids = published_periodical.values_list('article_id', flat=True)
+    published_event_ids = published_event.values_list('article_id', flat=True)
+    published_ids = list(chain(published_periodical_ids, published_event_ids))
+    accepted_ids = accepted.values_list('article_id', flat=True).exclude(article_id__in=published_ids)
+    submitted_ids = submitted.values_list('article_id', flat=True).exclude(Q(article_id__in=published_ids) |
+                                                                           Q(article_id__in=accepted_ids))
+    draft_ids = draft.values_list('article_id', flat=True).exclude(Q(article_id__in=published_ids) |
+                                                                   Q(article_id__in=accepted_ids) |
+                                                                   Q(article_id__in=submitted_ids))
+
+    # Articles from the scientific team
+    published_scientific = published_periodical.filter(article__team='s')
+    accepted_scientific = accepted.filter(article__type='p', article__team='s', article_id__in=accepted_ids)
+    submitted_scientific = submitted.filter(article__team='s', article_id__in=submitted_ids)
+    draft_scientific = draft.filter(article__team='s', article_id__in=draft_ids)
+
+    # Articles from the dissemination team
+    published_dissemin = published_periodical.filter(article__team='d')
+    accepted_dissemin = accepted.filter(article__type='p', article__team='d', article_id__in=accepted_ids)
+    submitted_dissemin = submitted.filter(article__team='d', article_id__in=submitted_ids)
+    draft_dissemin = draft.filter(article__team='d', article_id__in=draft_ids)
+
+    # Articles from the technology transfer team
[…]

### 2016-04-01 research/tests.py
NIRA-66 - Update the unit tests for Research app ArXiv tests.

@@ -437,6 +437,18 @@ class ArticlesTest(TestCase):
         self.assertNotEqual('Published', self.accepted.current_status())
 
 
+class ArXivTest(TestCase):
+    """ Test method for ArXiv handler. This should work if arxiv doesn't change it's classes """
+
+    def setUp(self):
+        self.arxiv_url = 'http://arxiv.org/abs/1601.03704'
+        self.date = datetime.date(2016, 1, 14)
+
+    def test_arxiv(self):
+        date = arxiv(self.arxiv_url)
+        self.assertEqual(self.date, date)
+
+
 class ImportPaper(TestCase):
 
     def setUp(self):

### 2016-04-01 research/tests.py
NIRA-66 - Update the unit tests for Research app ArXiv tests, fixed.

@@ -4,7 +4,7 @@ from django.test import TestCase
 from django.test.client import RequestFactory
 from models import AcademicWork, TypeAcademicWork, Person, Article, Draft, Submitted, Accepted, PublishedInPeriodical, \
     Periodical
-from views import scholar, scholar_info, valid_date, now_plus_five_years
+from views import scholar, scholar_info, valid_date, now_plus_five_years, arxiv
 import datetime
 from django.core.files.uploadedfile import SimpleUploadedFile
 
@@ -439,7 +439,6 @@ class ArticlesTest(TestCase):
 
 class ArXivTest(TestCase):
     """ Test method for ArXiv handler. This should work if arxiv doesn't change it's classes """
-
     def setUp(self):
         self.arxiv_url = 'http://arxiv.org/abs/1601.03704'
         self.date = datetime.date(2016, 1, 14)

### 2016-04-04 research/tests.py
NIRA-66 - Update the unit tests for Research app Setting a dict to simulate a .ris file.

@@ -442,23 +442,89 @@ class ArXivTest(TestCase):
     def setUp(self):
         self.arxiv_url = 'http://arxiv.org/abs/1601.03704'
         self.date = datetime.date(2016, 1, 14)
+        self.wrong_date = datetime.date(2015, 1, 14)
 
     def test_arxiv(self):
         date = arxiv(self.arxiv_url)
         self.assertEqual(self.date, date)
+        self.assertNotEqual(self.wrong_date, date)
 
 
-class ImportPaper(TestCase):
+class ImportPaperTest(TestCase):
 
     def setUp(self):
         logged, self.user, self.factory = system_authentication(self)
+        self.paper_list = ['TY  - JOUR',
+                       'T1  - Infinite systems of interacting chains with memory of variable length\xe2\x80\x94a stochastic model for biological neural nets',
+                       'A1  - Galves, Antonio',
+                       'A1  - L\xc3\xb6cherbach, Eva',
+                       'JO  - Journal of Statistical Physics',
+                       'VL  - 151',
+                       'IS  - 5',
+                       'SP  - 896',
+                       'EP  - 921',
+                       'SN  - 0022-4715',
+                       'Y1  - 2013',
+                       'PB  - Springer',
+                       'ER  - ',
+                       '',
+                       '',
+                       'TY  - CONF',
+                       'T1  - Combining multivariate Markov chains',
+                       'A1  - Garc\xc3\xada, Jes\xc3\xbas E',
+                       'JO  - PROCEEDINGS OF THE INTERNATIONAL CONFERENCE ON NUMERICAL ANALYSIS AND APPLIED MATHEMATICS 2014 (ICNAAM-2014)',
+                       'VL  - 1648',
+                       'SP  - 060003',
+                       'SN  - 0094-243X',
+                       'Y1  - 2015',
+                       'PB  - AIP Publishing',
+                       'ER  - ',
+                       '',
+                       '',
+                       'TY  - JOUR',
+                       'T1  - Hydrodynamic limit for interacting neurons',
+                       'A1  - De Masi, Anna', 'A1  - Galves, Antonio',
+                       'A1  - L\xc3\xb6cherbach, Eva',
+                       'A1  - Presutti, Errico',
+                       'JO  - Journal of Statistical Physics',
+                       'VL  - 158',
+                       'IS  - 4',
+                       'SP  - 866',
+                       'EP  - 902',
+                       'SN  - 0022-4715',
+                       'Y1  - 2014',
+                       'PB  - Springer',
+                       'ER  - ',
[…]

### 2016-04-04 research/tests.py
NIRA-66 - Update the unit tests for Research app Setting a dict to simulate a .ris file, fixing content on SimpleUploadedFile.

@@ -524,7 +524,7 @@ class ImportPaperTest(TestCase):
         response = self.client.get(reverse('import_papers'))
         self.assertEqual(response.status_code, 200)
 
-        ris_file = SimpleUploadedFile('citations.ris', b'rb', content=self.paper_list)
+        ris_file = SimpleUploadedFile('citations.ris', content=self.paper_list)
         response = self.client.post(reverse('import_papers'), {'file': ris_file})
         self.assertEqual(response.status_code, 200)
 

### 2016-04-04 templates/report/research/tex/articles.tex
NIRA-60 - Create an article report in Latex format

@@
+{% autoescape off %}
 {% block content %}
@@
 \subsubsection{Published or accepted}
+\begin{enumerate}
 		{% if published_scientific %}
-\begin{enumerate}
 			{% for article in published_scientific %}
-				{% if not article.article.hide %} \item {% if article.article.url %} \textbf{ \href{ {{ article.article.url }} }{ {{ article.article.title }}.
-} }{% else %}{{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors  %} \textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %} {{ article.article.authors }} {{ article.article.periodical }},{% endif %}{% if article.volume %} \textbf{ {{ article.volume }} }{% endif %}{% if article.number %} ({{ article.number }}),{% endif %}{% if article.start_page and article.end_page %} {{ article.start_page }}-{{ article.end_page }},{% endif %} {% if article.doi %}DOI: {{ article.doi }},{% endif %} {{ article.date|date:"Y" }}.{% endif %}
+				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %}{{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %} {{ article.article.authors }}.
+{{ article.article.periodical }},{% endif %}{% if article.volume %}\textbf{ {{ article.volume }} }{% endif %}{% if article.number %} ({{ article.number }}),{% endif %}{% if article.start_page and article.end_page %} {{ article.start_page }}-{{ article.end_page }},{% endif %} {% if article.doi %}DOI: {{ article.doi }},{% endif %} {{ article.date|date:"Y" }}.{% endif %}
 			{% endfor %}
+		{% endif %}
+		{% if accepted_scientific %}
+			{% for article in accepted_scientific %}
+				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %}{{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %} {{ article.article.authors }}.
+{{ article.article.periodical }},{% endif %} {{ article.date|date:"Y" }}, to appear.{% endif %}
+			{% endfor %}
+		{% endif %}
 \end{enumerate}
 	{% endif %}
+
+	{% if published_dissemin or accepted_dissemin %}
+\subsubsection{Published or accepted from the dissemination team}
+\begin{enumerate}
+		{% if published_dissemin %}
+			{% for article in published_dissemin %}
+				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %}{{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %} {{ article.article.authors }}.
+{{ article.article.periodical }},{% endif %}{% if article.volume %}\textbf{ {{ article.volume }} }{% endif %}{% if article.number %} ({{ article.number }}),{% endif %}{% if article.start_page and article.end_page %} {{ article.start_page }}-{{ article.end_page }},{% endif %} {% if article.doi %}DOI: {{ article.doi }},{% endif %} {{ article.date|date:"Y" }}.{% endif %}
+			{% endfor %}
+		{% endif %}
+		{% if accepted_dissemin %}
+			{% for article in accepted_scientific %}
+				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %}{{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %} {{ article.article.authors }}.
+{{ article.article.periodical }},{% endif %} {{ article.date|date:"Y" }}, to appear.{% endif %}
+			{% endfor %}
+		{% endif %}
+\end{enumerate}
+	{% endif %}
+
+	{% if published_tec_trans or accepted_tec_trans %}
+\subsubsection{Published or accepted from the technological transfer team}
+\begin{enumerate}
+		{% if published_tec_trans %}
+			{% for article in published_tec_trans %}
+				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %}{{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %} {{ article.article.authors }}.
+{{ article.article.periodical }},{% endif %}{% if article.volume %}\textbf{ {{ article.volume }} }{% endif %}{% if article.number %} ({{ article.number }}),{% endif %}{% if article.start_page and article.end_page %} {{ article.start_page }}-{{ article.end_page }},{% endif %} {% if article.doi %}DOI: {{ article.doi }},{% endif %} {{ article.date|date:"Y" }}.{% endif %}
+			{% endfor %}
+		{% endif %}
+		{% if accepted_tec_trans %}
+			{% for article in accepted_tec_trans %}
+				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %}{{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %} {{ article.article.authors }}.
+{{ article.article.periodical }},{% endif %} {{ article.date|date:"Y" }}, to appear.{% endif %}
+			{% endfor %}
+		{% endif %}
+\end{enumerate}
 	{% endif %}
@@
 {% endblock %}
+{% endautoescape %}

### 2016-04-04 research/tests.py
NIRA-66 - Update the unit tests for Research app Uploading a .ris file for testing.

@@ -454,78 +454,13 @@ class ImportPaperTest(TestCase):
 
     def setUp(self):
         logged, self.user, self.factory = system_authentication(self)
-        self.paper_list = ['TY  - JOUR',
-                       'T1  - Infinite systems of interacting chains with memory of variable length\xe2\x80\x94a stochastic model for biological neural nets',
-                       'A1  - Galves, Antonio',
-                       'A1  - L\xc3\xb6cherbach, Eva',
-                       'JO  - Journal of Statistical Physics',
-                       'VL  - 151',
-                       'IS  - 5',
-                       'SP  - 896',
-                       'EP  - 921',
-                       'SN  - 0022-4715',
-                       'Y1  - 2013',
-                       'PB  - Springer',
-                       'ER  - ',
-                       '',
-                       '',
-                       'TY  - CONF',
-                       'T1  - Combining multivariate Markov chains',
-                       'A1  - Garc\xc3\xada, Jes\xc3\xbas E',
-                       'JO  - PROCEEDINGS OF THE INTERNATIONAL CONFERENCE ON NUMERICAL ANALYSIS AND APPLIED MATHEMATICS 2014 (ICNAAM-2014)',
-                       'VL  - 1648',
-                       'SP  - 060003',
-                       'SN  - 0094-243X',
-                       'Y1  - 2015',
-                       'PB  - AIP Publishing',
-                       'ER  - ',
-                       '',
-                       '',
-                       'TY  - JOUR',
-                       'T1  - Hydrodynamic limit for interacting neurons',
-                       'A1  - De Masi, Anna', 'A1  - Galves, Antonio',
-                       'A1  - L\xc3\xb6cherbach, Eva',
-                       'A1  - Presutti, Errico',
-                       'JO  - Journal of Statistical Physics',
-                       'VL  - 158',
-                       'IS  - 4',
-                       'SP  - 866',
-                       'EP  - 902',
-                       'SN  - 0022-4715',
-                       'Y1  - 2014',
-                       'PB  - Springer',
-                       'ER  - ',
-                       '',
-                       '',
-                       'TY  - JOUR',
-                       'T1  - Computationally efficient change point detection for high-dimensional regression',
-                       'A1  - Leonardi, Florencia',
-                       'A1  - B\xc3\xbchlmann, Peter',
-                       'JO  - arXiv preprint arXiv:1601.03704',
-                       'Y1  - 2016',
-                       'ER  -',
[…]

### 2016-04-04 templates/report/research/tex/articles.tex
NIRA-60 - Create an article report in Latex format

--- 2016-04-01 templates/report/research/tex/articles.tex
@@
 {% if published_scientific or accepted_scientific or submitted_scientific or draft_scientific or published_dissemin or accepted_dissemin or submitted_dissemin or draft_dissemin or published_tec_trans or accepted_tec_trans or submitted_tec_trans or draft_tec_trans or published_scientific_in_event or accepted_scientific_in_event or published_dissemin_in_event or accepted_dissemin_in_event or published_tec_trans_in_event or accepted_tec_trans_in_event%}
-
 	{% if published_scientific or accepted_scientific %}
-\subsubsection{Published or accepted}
+\paragraph{Published or Accepted}
+\begin{enumerate}
 		{% if published_scientific %}
-\begin{enumerate}
 			{% for article in published_scientific %}
-				{% if not article.article.hide %} \item {% if article.article.url %} \textbf{ \href{ {{ article.article.url }} }{ {{ article.article.title }}.
-} }{% else %}{{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors  %} \textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %} {{ article.article.authors }} {{ article.article.periodical }},{% endif %}{% if article.volume %} \textbf{ {{ article.volume }} }{% endif %}{% if article.number %} ({{ article.number }}),{% endif %}{% if article.start_page and article.end_page %} {{ article.start_page }}-{{ article.end_page }},{% endif %} {% if article.doi %}DOI: {{ article.doi }},{% endif %} {{ article.date|date:"Y" }}.{% endif %}
+				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} {{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.periodical }},{% endif %}{% if article.volume %}\textbf{ {{ article.volume }} }{% endif %}{% if article.number %} ({{ article.number }}),{% endif %}{% if article.start_page and article.end_page %} {{ article.start_page }}-{{ article.end_page }},{% endif %} {% if article.doi %}DOI: {{ article.doi }},{% endif %} {{ article.date|date:"Y" }}.{% endif %}
 			{% endfor %}
-\end{enumerate}
+		{% endif %}
+		{% if accepted_scientific %}
+			{% for article in accepted_scientific %}
+				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} {{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.periodical }},{% endif %} {{ article.date|date:"Y" }}, to appear.{% endif %}
+			{% endfor %}
 		{% endif %}
 	{% endif %}
+
+	{% if published_dissemin or accepted_dissemin %}
+\vspace{0.5cm}
+\hspace{-1cm}\noindent{\bf Published or accepted from the dissemination team}
+		{% if published_dissemin %}
+			{% for article in published_dissemin %}
+				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} {{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.periodical }},{% endif %}{% if article.volume %}\textbf{ {{ article.volume }} }{% endif %}{% if article.number %} ({{ article.number }}),{% endif %}{% if article.start_page and article.end_page %} {{ article.start_page }}-{{ article.end_page }},{% endif %} {% if article.doi %}DOI: {{ article.doi }},{% endif %} {{ article.date|date:"Y" }}.{% endif %}
+			{% endfor %}
+		{% endif %}
+		{% if accepted_dissemin %}
+			{% for article in accepted_dissemin %}
+				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} {{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.periodical }},{% endif %} {{ article.date|date:"Y" }}, to appear.{% endif %}
+			{% endfor %}
+		{% endif %}
+	{% endif %}
+
+	{% if published_tec_trans or accepted_tec_trans %}
+\vspace{0.5cm}
+\hspace{-1cm}\noindent{\bf Published or accepted from the technological transfer team}
+		{% if published_tec_trans %}
+			{% for article in published_tec_trans %}
+				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} {{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.periodical }},{% endif %}{% if article.volume %}\textbf{ {{ article.volume }} }{% endif %}{% if article.number %} ({{ article.number }}),{% endif %}{% if article.start_page and article.end_page %} {{ article.start_page }}-{{ article.end_page }},{% endif %} {% if article.doi %}DOI: {{ article.doi }},{% endif %} {{ article.date|date:"Y" }}.{% endif %}
+			{% endfor %}
+		{% endif %}
+		{% if accepted_tec_trans %}
+			{% for article in accepted_tec_trans %}
+				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} {{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.periodical }},{% endif %} {{ article.date|date:"Y" }}, to appear.{% endif %}
+			{% endfor %}
+		{% endif %}
+	{% endif %}
+
+	{% if submitted_scientific %}
+\vspace{0.5cm}
+\hspace{-1cm}\noindent{\bf Submitted}
+		{% for article in submitted_scientific %}
+			{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} {{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{% else %}\textit{ {{ article.article.authors }}.}{% endif %}{% endif %}
+		{% endfor %}
+	{% endif %}
+
+	{% if submitted_dissemin %}
+\vspace{0.5cm}
+\hspace{-1cm}\noindent{\bf Submitted from the dissemination team}
+		{% for article in submitted_dissemin %}
+			{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} {{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{% else %}\textit{ {{ article.article.authors }}.}{% endif %}{% endif %}
+		{% endfor %}
+	{% endif %}
+
+	{% if submitted_tec_trans %}
+\vspace{0.5cm}
+\hspace{-1cm}\noindent{\bf Submitted from the technological transfer team}
+		{% for article in submitted_tec_trans %}
+			{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} {{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{% else %}\textit{ {{ article.article.authors }}.}{% endif %}{% endif %}
+		{% endfor %}
+	{% endif %}
+
+	{% if published_scientific_in_event or accepted_scientific_in_event %}
+\vspace{0.5cm}
+\hspace{-1cm}\noindent{\bf Communications in meetings with referee}
+		{% if published_scientific_in_event %}
+			{% for article in published_scientific_in_event %}
+				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} {{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.event }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.event }},{% endif %}{% if article.article.event.acronym %} {{ article.article.event.acronym }}{% endif %}, {{ article.article.event.local }}, {% if article.article.event.start_date|date:"M" == article.article.event.end_date|date:"M" %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"d, Y" }}{% else %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"M d, Y" }}.{% endif %}{% endif %}
+			{% endfor %}
+		{% endif %}
+		{% if accepted_scientific_in_event %}
+			{% for article in published_scientific_in_event %}
+				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} {{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.event }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.event }},{% endif %}{% if article.article.event.acronym %} {{ article.article.event.acronym }}{% endif %}, {{ article.article.event.local }}, {% if article.article.event.start_date|date:"M" == article.article.event.end_date|date:"M" %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"d, Y" }}, to be held{% else %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"M d, Y" }}, to be held{% endif %}.{% endif %}
+			{% endfor %}
+		{% endif %}
+	{% endif %}
+
+	{% if published_dissemin_in_event or accepted_dissemin_in_event %}
+\vspace{0.5cm}
+\hspace{-1cm}\noindent{\bf Communications in meetings with referee from the dissemination team}
+		{% if published_dissemin_in_event %}
+			{% for article in published_dissemin_in_event %}
+				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} {{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.event }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.event }},{% endif %}{% if article.article.event.acronym %} {{ article.article.event.acronym }}{% endif %}, {{ article.article.event.local }}, {% if article.article.event.start_date|date:"M" == article.article.event.end_date|date:"M" %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"d, Y" }}{% else %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"M d, Y" }}.{% endif %}{% endif %}
+			{% endfor %}
+		{% endif %}
+		{% if accepted_dissemin_in_event %}
+			{% for article in accepted_dissemin_in_event %}
+				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} {{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.event }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.event }},{% endif %}{% if article.article.event.acronym %} {{ article.article.event.acronym }}{% endif %}, {{ article.article.event.local }}, {% if article.article.event.start_date|date:"M" == article.article.event.end_date|date:"M" %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"d, Y" }}, to be held{% else %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"M d, Y" }}, to be held{% endif %}.{% endif %}
+			{% endfor %}
+		{% endif %}
+	{% endif %}
+
+	{% if published_tec_trans_in_event or accepted_tec_trans_in_event %}
+\vspace{0.5cm}
+\hspace{-1cm}\noindent{\bf Communications in meetings with referee from the technological transfer team}
+		{% if published_tec_trans_in_event %}
+			{% for article in published_tec_trans_in_event %}
+				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} {{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.event }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.event }},{% endif %}{% if article.article.event.acronym %} {{ article.article.event.acronym }}{% endif %}, {{ article.article.event.local }}, {% if article.article.event.start_date|date:"M" == article.article.event.end_date|date:"M" %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"d, Y" }}{% else %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"M d, Y" }}.{% endif %}{% endif %}
+			{% endfor %}
+		{% endif %}
+		{% if accepted_tec_trans_in_event %}
+			{% for article in accepted_tec_trans_in_event %}
+				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} {{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.event }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.event }},{% endif %}{% if article.article.event.acronym %} {{ article.article.event.acronym }}{% endif %}, {{ article.article.event.local }}, {% if article.article.event.start_date|date:"M" == article.article.event.end_date|date:"M" %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"d, Y" }}, to be held{% else %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"M d, Y" }}, to be held{% endif %}.{% endif %}
+			{% endfor %}
+		{% endif %}
+	{% endif %}
+
+	{% if draft_scientific %}
+\vspace{0.5cm}
+\hspace{-1cm}\noindent{\bf Drafts}
+		{% for article in draft_scientific %}
+			{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} {{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{% else %}\textit{ {{ article.article.authors }}.}{% endif %}{% endif %}
+		{% endfor %}
+	{% endif %}
+
+	{% if draft_dissemin %}
+\vspace{0.5cm}
+\hspace{-1cm}\noindent{\bf Drafts from the dissemination team}
+		{% for article in draft_dissemin %}
+			{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} {{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{% else %}\textit{ {{ article.article.authors }}.}{% endif %}{% endif %}
+		{% endfor %}
+	{% endif %}
+
+	{% if draft_tec_trans %}
+\vspace{0.5cm}
+\hspace{-1cm}\noindent{\bf Drafts from the technological transfer team}
+		{% for article in draft_tec_trans %}
+			{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} {{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{% else %}\textit{ {{ article.article.authors }}.}{% endif %}{% endif %}
+		{% endfor %}
+	{% endif %}
+\end{enumerate}
 

### 2016-04-04 research/tests.py
NIRA-66 - Update the unit tests for Research app Tests for other views responses.

@@ -1,7 +1,6 @@
 from custom_auth.models import User
 from django.core.urlresolvers import reverse
 from django.test import TestCase
-from django.test.client import RequestFactory
 from models import AcademicWork, TypeAcademicWork, Person, Article, Draft, Submitted, Accepted, PublishedInPeriodical, \
     Periodical
 from views import scholar, scholar_info, valid_date, now_plus_five_years, arxiv
@@ -457,6 +456,7 @@ class ImportPaperTest(TestCase):
         self.assertEqual(logged, True)
 
     def test_import_file(self):
+
         response = self.client.get(reverse('import_papers'))
         self.assertEqual(response.status_code, 200)
 
@@ -466,3 +466,14 @@ class ImportPaperTest(TestCase):
         not_ris_file = SimpleUploadedFile('citations.jpg', b'rb', content_type='image/jpeg')
         response = self.client.post(reverse('import_papers'), {'file': not_ris_file})
         self.assertEqual(response.status_code, 200)
+
+        response = self.client.post(reverse('add_periodicals'), {'action': 'add'})
+        self.assertEqual(response.status_code, 200)
+
+        #Problems with cache on this step
+        #response = self.client.post(reverse('add_periodicals'), {'action': 'next'})
+        #self.assertEqual(response.status_code, 200)
+
+        # Redirect status
+        response = self.client.post(reverse('add_periodicals'), {'action': 'back'})
+        self.assertEqual(response.status_code, 302)

### 2016-04-04 research/tests.py
NIRA-66 - Update the unit tests for Research app Added RequestFactory().

@@ -1,6 +1,6 @@
 from custom_auth.models import User
 from django.core.urlresolvers import reverse
-from django.test import TestCase
+from django.test import TestCase, RequestFactory
 from models import AcademicWork, TypeAcademicWork, Person, Article, Draft, Submitted, Accepted, PublishedInPeriodical, \
     Periodical
 from views import scholar, scholar_info, valid_date, now_plus_five_years, arxiv

### 2016-04-04 research/tests.py
NIRA-66 - Update the unit tests for Research app: Tests for views responses.

@@ -474,6 +474,100 @@ class ImportPaperTest(TestCase):
         #response = self.client.post(reverse('add_periodicals'), {'action': 'next'})
         #self.assertEqual(response.status_code, 200)
 
+
+class AddPeriodicalsTest(TestCase):
+
+    def setUp(self):
+        logged, self.user, self.factory = system_authentication(self)
+        self.assertEqual(logged, True)
+
+    def test_add_periodicals(self):
+
         # Redirect status
         response = self.client.post(reverse('add_periodicals'), {'action': 'back'})
+        self.assertEqual(response.status_code, 302)
+
+
+class AddPapersTest(TestCase):
+
+    def setUp(self):
+        logged, self.user, self.factory = system_authentication(self)
+        self.assertEqual(logged, True)
+
+    def test_add_papers(self):
+
+        # Cache problems
+        #response = self.client.post(reverse('add_papers'), {'action': 'next'})
+        #self.assertEqual(response.status_code, 200)
+
+        response = self.client.post(reverse('add_papers'), {'action': 'back'})
+        self.assertEqual(response.status_code, 200)
+
+
+class PeriodicalPublishedTest(TestCase):
+
+    def setUp(self):
+        logged, self.user, self.factory = system_authentication(self)
+        self.assertEqual(logged, True)
+
+    def test_periodical_published_papers(self):
+
+        response = self.client.post(reverse('periodical_published_papers'), {'action': 'add'})
+        self.assertEqual(response.status_code, 200)
+
+        response = self.client.post(reverse('periodical_published_papers'), {'action': 'next'})
+        self.assertEqual(response.status_code, 200)
+
+
+class ArxivPapersTest(TestCase):
+
+    def setUp(self):
+        logged, self.user, self.factory = system_authentication(self)
+        self.assertEqual(logged, True)
+
+    def test_arxiv_papers(self):
+
+        response = self.client.post(reverse('arxiv_papers'), {'action': 'add'})
+        self.assertEqual(response.status_code, 200)
+
+        response = self.client.post(reverse('arxiv_papers'), {'action': 'next'})
+        self.assertEqual(response.status_code, 200)
+
+        response = self.client.post(reverse('arxiv_papers'), {'action': 'back'})
+        self.assertEqual(response.status_code, 200)
+
+
+class EventPapersTest(TestCase):
+
+    def setUp(self):
+        logged, self.user, self.factory = system_authentication(self)
+        self.assertEqual(logged, True)
+
[…]

### 2016-04-04 research/tests.py
NIRA-66 - Update the unit tests for Research app: Fixing some violations...

@@ -1,10 +1,10 @@
+import datetime
 from custom_auth.models import User
 from django.core.urlresolvers import reverse
 from django.test import TestCase, RequestFactory
-from models import AcademicWork, TypeAcademicWork, Person, Article, Draft, Submitted, Accepted, PublishedInPeriodical, \
+from research.models import AcademicWork, TypeAcademicWork, Person, Article, Draft, Submitted, Accepted, PublishedInPeriodical, \
     Periodical
-from views import scholar, scholar_info, valid_date, now_plus_five_years, arxiv
-import datetime
+from research.views import scholar, scholar_info, valid_date, now_plus_five_years, arxiv
 from django.core.files.uploadedfile import SimpleUploadedFile
 
 

### 2016-04-04 research/tests.py
NIRA-66 - Update the unit tests for Research app: Fixing some violations... Part 2.

@@ -2,8 +2,8 @@ import datetime
 from custom_auth.models import User
 from django.core.urlresolvers import reverse
 from django.test import TestCase, RequestFactory
-from research.models import AcademicWork, TypeAcademicWork, Person, Article, Draft, Submitted, Accepted, PublishedInPeriodical, \
-    Periodical
+from research.models import AcademicWork, TypeAcademicWork, Person, Article, Draft, Submitted, Accepted, \
+PublishedInPeriodical, Periodical
 from research.views import scholar, scholar_info, valid_date, now_plus_five_years, arxiv
 from django.core.files.uploadedfile import SimpleUploadedFile
 
@@ -470,9 +470,9 @@ class ImportPaperTest(TestCase):
         response = self.client.post(reverse('add_periodicals'), {'action': 'add'})
         self.assertEqual(response.status_code, 200)
 
-        #Problems with cache on this step
-        #response = self.client.post(reverse('add_periodicals'), {'action': 'next'})
-        #self.assertEqual(response.status_code, 200)
+        # Problems with cache on this step
+        # response = self.client.post(reverse('add_periodicals'), {'action': 'next'})
+        # self.assertEqual(response.status_code, 200)
 
 
 class AddPeriodicalsTest(TestCase):
@@ -497,8 +497,8 @@ class AddPapersTest(TestCase):
     def test_add_papers(self):
 
         # Cache problems
-        #response = self.client.post(reverse('add_papers'), {'action': 'next'})
-        #self.assertEqual(response.status_code, 200)
+        # response = self.client.post(reverse('add_papers'), {'action': 'next'})
+        # self.assertEqual(response.status_code, 200)
 
         response = self.client.post(reverse('add_papers'), {'action': 'back'})
         self.assertEqual(response.status_code, 200)
@@ -562,6 +562,7 @@ class UpdatePapersTest(TestCase):
         self.assertEqual(logged, True)
 
     def test_update_papers(self):
+
         response = self.client.post(reverse('update_papers'), {'action': 'update'})
         self.assertEqual(response.status_code, 200)
 

### 2016-04-13 research/models.py
NIRA-80 - In article page, return authors from ris_file_authors field or from CitationName class

@@ -1,7 +1,6 @@
 from django.db import models
 from django.utils.translation import ugettext_lazy as _
 from person.models import Person, Institution, CitationName
-from django.utils.html import format_html
 
 
 # Defining types of research results
@@ -55,10 +54,8 @@ class ResearchResult(models.Model):
         if self.ris_file_authors != '':
             return self.ris_file_authors
         else:
-            return format_html('; '.join([person.citation_name if person.citation_name else person.full_name
-                                          for person in self.person.all()]))
-
-    authors.allow_tags = True
+            return '; '.join([unicode(name) for name in CitationName.objects.filter(person_id__in=self.person.all(),
+                                                                                    default_name=True)])
 
 
 class Author(models.Model):

### 2016-04-13 person/migrations/0002_citationname.py
Added migrations file

@@ -1,0 +1,29 @@
+# -*- coding: utf-8 -*-
+from __future__ import unicode_literals
+
+from django.db import models, migrations
+
+
+class Migration(migrations.Migration):
+
+    dependencies = [
+        ('person', '0001_initial'),
+    ]
+
+    operations = [
+        migrations.CreateModel(
+            name='CitationName',
+            fields=[
+                ('id', models.AutoField(verbose_name='ID', serialize=False, auto_created=True, primary_key=True)),
+                ('name', models.CharField(max_length=255, verbose_name='Name in bibliographic citation')),
+                ('default_name', models.BooleanField(default=False, max_length=3, verbose_name='Default name?', choices=[(True, 'Yes'), (False, 'No')])),
+                ('person', models.ForeignKey(verbose_name='Name', to='person.Person')),
+            ],
+            options={
+                'ordering': ('person',),
+                'verbose_name': 'Citation name',
+                'verbose_name_plural': 'Citation name',
+            },
+            bases=(models.Model,),
+        ),
+    ]

### 2016-04-13 person/admin.py
citation_name field removed from Person class

@@ -10,7 +10,7 @@ admin.site.register(InstitutionType)
 class PersonAdmin(admin.ModelAdmin):
     fieldsets = (
         (None, {
-            'fields': ['full_name', 'email', 'citation_name', 'role', 'institution']
+            'fields': ['full_name', 'email', 'role', 'institution']
         }),
         (None, {
             'fields': ('rg', 'cpf', 'passport')

### 2016-04-13 person/migrations/0003_remove_person_citation_name.py

@@ -1,0 +1,18 @@
+# -*- coding: utf-8 -*-
+from __future__ import unicode_literals
+
+from django.db import models, migrations
+
+
+class Migration(migrations.Migration):
+
+    dependencies = [
+        ('person', '0002_citationname'),
+    ]
+
+    operations = [
+        migrations.RemoveField(
+            model_name='person',
+            name='citation_name',
+        ),
+    ]

### 2016-04-13 person/models.py

@@ -133,8 +133,6 @@ class Person(models.Model):
     institution = models.ForeignKey(Institution, verbose_name=_('Institution'), blank=True, null=True)
     full_name = models.CharField(_('Full name'), unique=True, max_length=255)
     email = models.EmailField(_('Email'), blank=True, null=True)
-    citation_name = models.CharField(_('Name in bibliographic citation'), max_length=255, blank=True, null=True,
-                                     help_text='E.g.: Silva, J.')
     rg = models.CharField(_('RG'), max_length=12, blank=True, null=True)
     cpf = models.CharField(_('CPF'), blank=True, null=True, max_length=15, validators=[validate_cpf])
     passport = models.CharField(_('Passport'), max_length=12, blank=True, null=True)

### 2016-04-14 templates/report/research/tex/articles.tex
NIRA-83 - Create a view to generate the citation names Created the generator of citation names.

@@
 {% block content %}
+
+{% with lb="{" rb="}" %}
 
@@
 			{% for article in published_scientific %}
-				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} {{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.periodical }},{% endif %}{% if article.volume %}\textbf{ {{ article.volume }} }{% endif %}{% if article.number %} ({{ article.number }}),{% endif %}{% if article.start_page and article.end_page %} {{ article.start_page }}-{{ article.end_page }},{% endif %} {% if article.doi %}DOI: {{ article.doi }},{% endif %} {{ article.date|date:"Y" }}.{% endif %}
+				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{{ '{' }}{{ article.article.url }}{{ '}' }} }{ {{ article.article.title }}.} }{% else %} {{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.periodical }},{% endif %}{% if article.volume %}\textbf{ {{ article.volume }} }{% endif %}{% if article.number %} ({{ article.number }}),{% endif %}{% if article.start_page and article.end_page %} {{ article.start_page }}-{{ article.end_page }},{% endif %} {% if article.doi %}DOI: {{ article.doi }},{% endif %} {{ article.date|date:"Y" }}.{% endif %}
 			{% endfor %}
@@
 
+{% endwith %}
 {% endblock %}

### 2016-04-14 person/views.py

@@ -1,20 +1,104 @@
-from person.models import University, Institute
+# -*- coding: utf-8 -*-
+from django.shortcuts import render
+from person.models import Person, CitationName
 from django.contrib.auth.decorators import login_required
-from django.http import HttpResponse
-from django.shortcuts import get_object_or_404
-import json as simplejson
+
+
+prep = ['da', 'do', 'de', 'dos']
+
+
+def first_letter_of_the_name(names):
+    letter = ''
+    last_name = names[-1]
+    for name in names:
+        if name != last_name and name not in prep:
+            letter += name[0]
+    return letter
+
+
+def names_without_last_name(names):
+    last_name = names[-1]
+    citation_name = [name for name in names if name != last_name and name not in prep]
+    citation_name = ' '.join(citation_name)
+    return citation_name
+
+
+def first_name_and_first_letter(names):
+    first_letter = ''
+    first_name = names[0]
+    last_name = names[-1]
+    for name in names:
+        if name != first_name and name != last_name and name not in prep:
+            first_letter += name[0]
+    if first_letter != '':
+        citation_name = first_name+' '+first_letter
+        return citation_name
+    else:
+        citation_name = first_name
+        return citation_name
+
+
+def generate_citation_names(person):
+
+    # Get full name and id from person.
+        full_name = person.full_name
+        person_id = person.pk
+
+        # Split the full name.
+        split_name = full_name.split()
+
+        # Get the last name
+        last_name = split_name[-1]
+
+        # Get the first letter of the name except the last name
+        letters = first_letter_of_the_name(split_name)
+
+        # Get names without last name
+        almost_full_name = names_without_last_name(split_name)
+
+        # Get first name and first letter of the middle name
+        first_name_letter_middle_name = first_name_and_first_letter(split_name)
+
+        # Imagine a person called João Carlos da Silva.
+        # Here the citation would be "Silva, JC"
+        citation_name_01 = CitationName(person_id=person_id, name=last_name+','+' '+letters)
+        if CitationName.objects.filter(person_id=person_id, name=citation_name_01).exists() is False:
+            citation_name_01.save()
+
+        # Here the citation would be "Silva, João Carlos"
+        citation_name_02 = CitationName(person_id=person_id, name=last_name+','+' '+almost_full_name)
+        if CitationName.objects.filter(person_id=person_id, name=citation_name_02).exists() is False:
+            citation_name_02.save()
+
+        # Here the citation would be "Silva, João C"
[…]

### 2016-04-14 sistema/urls.py

@@ -19,6 +19,7 @@ urlpatterns = patterns(
     url(r'^order/', include('order.urls')),
     url(r'^activity/', include('activity.urls')),
     url(r'^research/', include('research.urls')),
+    url(r'^person/', include('person.urls')),
     url(r'^dissemination/', include('dissemination.urls')),
 ) + static(settings.MEDIA_URL, document_root=settings.MEDIA_ROOT)
 

### 2016-04-14 person/views.py
NIRA-83 - Create a view to generate the citation names Fixed the redirect to index.html

@@ -1,98 +1,134 @@
 # -*- coding: utf-8 -*-
-from django.shortcuts import render
-from person.models import Person, CitationName
+from django.contrib import messages
 from django.contrib.auth.decorators import login_required
+from django.core.urlresolvers import reverse
+from django.shortcuts import redirect
+from django.utils.translation import ugettext_lazy as _
+from person.models import Person, CitationName
+
+prep = ['e', 'da', 'do', 'de', 'dos', 'E', 'Da', 'Do', 'De', 'Dos']
 
 
-prep = ['da', 'do', 'de', 'dos']
-
-
-def first_letter_of_the_name(names):
-    letter = ''
+def name_with_first_letters(names, with_prep):
+    letters = ''
     last_name = names[-1]
+    last_name_with_prep = names[-2]+' '+last_name
+
     for name in names:
         if name != last_name and name not in prep:
-            letter += name[0]
-    return letter
+            letters += name[0]
+
+    if not with_prep:
+        return last_name+','+' '+letters
+    else:
+        return last_name_with_prep+','+' '+letters
 
 
-def names_without_last_name(names):
+def names_without_last_name(names, with_prep):
     last_name = names[-1]
+    last_name_with_prep = names[-2]+' '+last_name
     citation_name = [name for name in names if name != last_name and name not in prep]
     citation_name = ' '.join(citation_name)
-    return citation_name
+
+    if not with_prep:
+        return last_name+','+' '+citation_name
+
+    else:
+        return last_name_with_prep+','+' '+citation_name
 
 
-def first_name_and_first_letter(names):
+def first_name_and_first_letter(names, with_prep):
     first_letter = ''
     first_name = names[0]
     last_name = names[-1]
+    last_name_with_prep = names[-2]+' '+last_name
+
     for name in names:
         if name != first_name and name != last_name and name not in prep:
             first_letter += name[0]
-    if first_letter != '':
-        citation_name = first_name+' '+first_letter
-        return citation_name
+
+    if not with_prep:
+        if first_letter != '':
+            citation_name = first_name+' '+first_letter
+            return last_name+','+' '+citation_name
+        else:
+            citation_name = first_name
+            return last_name+','+' '+citation_name
+
     else:
-        citation_name = first_name
-        return citation_name
+        if first_letter != '':
+            citation_name = first_name+' '+first_letter
+            return last_name_with_prep+','+' '+citation_name
+        else:
+            citation_name = first_name
[…]

### 2016-04-15 research/admin.py
NIRA-86 - Update the "Academic Work" class according to João's suggestions

@@ -1,9 +1,8 @@
 from django.contrib import admin
-from research.models import *
-#from forms import ArticleAdminForm, BookAdminForm, AuthorsInlineFormset
-from forms import ArticleAdminForm, BookAdminForm
 from django.db.models import Q
 from django.utils.translation import ugettext_lazy as _
+from forms import ArticleAdminForm, BookAdminForm, AcademicWorkAdminForm
+from research.models import *
 
 
 admin.site.register(TypeAcademicWork)
@@ -68,7 +67,8 @@ class ArticleAdmin(SuperResearchResult):
     fields = ['team', 'title', 'status', 'type', 'periodical', 'event', 'url', 'ris_file_authors', 'hide', 'note']
     list_display = ('team', 'title', 'authors', 'current_status', 'type_of_article')
     list_display_links = ('title',)
-    inlines = (AuthorsInline, DraftInline, SubmittedInline, AcceptedInline, PublishedInline, PublishedInPeriodicalInline)
+    inlines = (AuthorsInline, DraftInline, SubmittedInline, AcceptedInline, PublishedInline,
+               PublishedInPeriodicalInline)
     form = ArticleAdminForm
 
 admin.site.register(Article, ArticleAdmin)
@@ -104,9 +104,11 @@ admin.site.register(Book, BookAdmin)
 
 
 class AcademicWorkAdmin(admin.ModelAdmin):
-    fields = ['type', 'title', 'advisee', 'advisor', 'co_advisor', 'schollarship', 'start_date', 'end_date']
+    fields = ['type', 'title', 'advisee', 'advisor', 'co_advisor', 'funding', 'funding_agency', 'start_date',
+              'end_date', 'url', 'abstract']
     list_display = ('title', 'advisee', 'advisor', 'type', 'start_date', 'end_date')
     list_display_links = ('title',)
+    form = AcademicWorkAdminForm
 
     # Shows the academic work according to the user permission
     # No restriction for users defined as superuser or NIRA Admin

### 2016-04-15 research/forms.py

@@ -1,5 +1,5 @@
 from django import forms
-from models import Article, Book
+from models import Article, Book, AcademicWork
 from django.forms import TextInput, CheckboxSelectMultiple
 from django.utils.translation import ugettext_lazy as _
 
@@ -33,6 +33,29 @@ class ArticleAdminForm(forms.ModelForm):
         }
 
 
+class BookAdminForm(forms.ModelForm):
+
+    class Meta:
+        model = Book
+        fields = ['type', 'chapter', 'start_page', 'end_page']
+
+    class Media:
+        js = ('/static/js/research.js',)
+
+
+class AcademicWorkAdminForm(forms.ModelForm):
+
+    class Meta:
+        model = AcademicWork
+        fields = ['url']
+        widgets = {
+            'url': TextInput(attrs={'size': 90, 'placeholder': 'http://example.com'}),
+        }
+
+    class Media:
+        js = ('/static/js/academic_works.js',)
+
+
 # class AuthorsInlineFormset(forms.models.BaseInlineFormSet):
 #     def clean(self):
 #         """Check that at least one author has been entered."""
@@ -42,13 +65,3 @@ class ArticleAdminForm(forms.ModelForm):
 #         if not any(cleaned_data and not cleaned_data.get('DELETE', False)
 #                    for cleaned_data in self.cleaned_data):
 #             raise forms.ValidationError(_('You must have at least one author'))
-
-
-class BookAdminForm(forms.ModelForm):
-
-    class Meta:
-        model = Book
-        fields = ['type', 'chapter', 'start_page', 'end_page']
-
-    class Media:
-        js = ('/static/js/research.js',)

### 2016-04-15 research/models.py

@@ -37,6 +37,8 @@ ARTICLE_TYPE = (
     (EVENT, _('Event (Conference, congress, meeting, etc)')),
 )
 
+FUNDING_CHOICES = ((True,'Yes'), (False, 'No'))
+
 
 class ResearchResult(models.Model):
     team = models.CharField(_('Team'), max_length=1, choices=TEAMS)
@@ -297,9 +299,12 @@ class AcademicWork(models.Model):
     advisor = models.ForeignKey(Person, verbose_name=_('Advisor'), related_name='advisor_academic_work')
     co_advisor = models.ManyToManyField(Person, verbose_name=_('Co-Advisor'), related_name='co_advisor_academic_work',
                                         blank=True, null=True)
-    schollarship = models.CharField(_('Schollarship'), max_length=255, blank=True, null=True)
+    funding = models.BooleanField(_('Financially supported?'), choices=FUNDING_CHOICES, max_length=3)
+    funding_agency = models.CharField(_('Funding agency'), max_length=255, blank=True)
+    url = models.URLField(_('URL'), max_length=255, blank=True, null=True, help_text='URL to funding information.')
     start_date = models.DateField(_('Start date'))
     end_date = models.DateField(_('End date'), blank=True, null=True)
+    abstract = models.TextField(_('Abstract'))
 
     def __unicode__(self):
         return u'%s' % self.title

### 2016-04-15 static/js/academic_works.js

@@ -1,0 +1,26 @@
+$(document).ready(function () {
+
+    // ### Book or chapter ###
+
+    var $id_type = $('#id_funding');
+
+    $id_type.each(function() {
+        if($(this).val() == 'True'){
+            $('#id_funding_agency').parents('.row').show();
+            $('#id_url').parents('.row').show();
+        } else{
+            $('#id_funding_agency').parents('.row').hide();
+            $('#id_url').parents('.row').hide();
+        }
+    });
+
+    $id_type.change(function(){
+        if($(this).val() == 'True'){
+            $('#id_funding_agency').parents('.row').show();
+            $('#id_url').parents('.row').show();
+        } else{
+            $('#id_funding_agency').parents('.row').hide();
+            $('#id_url').parents('.row').hide();
+        }
+    });
+});

### 2016-04-15 templates/report/research/tex/academic_works.tex
File created using the institution from the advisee.
NIRA-86 - Update the "Academic Work" class according to João's suggestions

@@
 		{% if result.co_advisors %}\item Co-advisor: {{ result.co_advisors }}{% endif %}
-		\item Institution: {{ result.institution }}
-		{% if result.schollarship %}\item Schollarship: {{ result.schollarship }}{% endif %}
+		\item Institution: {{ result.advisee.institution }}
+		{% if result.funding_agency %}\item Funding: {{ result.funding_agency }}{% endif %}
+		{% if result.url %}\item Funding information: {{ result.url }}{% endif %}
+		\item Abstract: {{ result.abstract }}
 	\end{itemize}
@@
 	\begin{itemize}
-		\item Period: {{ result.start_date }} - ongoing
+		\item Period: {{ result.start_date }} - ongoing {% if result.end_date %}(as of {{ result.end_date }}){% endif %}
 		\item Advisee: {{ result.advisee }}

### 2016-04-15 research/tests.py
NIRA-86 - Update the "Academic Work" class according to João's suggestions

@@ -25,7 +25,7 @@ def system_authentication(instance):
     return logged, user, factory
 
 
-def create_postdoc(type, title, advisee, advisor, start_date, end_date):
+def create_postdoc(type, title, advisee, advisor, start_date, end_date, abstract):
     postdoc = AcademicWork()
     postdoc.type = type
     postdoc.title = title
@@ -33,6 +33,7 @@ def create_postdoc(type, title, advisee, advisor, start_date, end_date):
     postdoc.advisor = advisor
     postdoc.start_date = start_date
     postdoc.end_date = end_date
+    postdoc.abstract = abstract
     postdoc.save()
     return postdoc
 
@@ -82,7 +83,7 @@ class ResearchTimelineTest(TestCase):
     academic_work = None
     advisee = None
     advisor = None
-
+    abstract = None
     team = None
 
     place_of_publication = None
@@ -139,6 +140,9 @@ class ResearchTimelineTest(TestCase):
         advisor = Person.objects.create(full_name='Emma Miller')
         advisor.save()
 
+        abstract = 'Mussum ipsum cacilds, vidis litro abertis. Consetis adipiscings elitis. Pra lá , depois divoltis ' \
+                   'porris, paradis. Paisis, filhis, espiritis santis.'
+
         team = "s"
 
         place_of_publication = Periodical.objects.create(name="Scientific America")
@@ -147,28 +151,36 @@ class ResearchTimelineTest(TestCase):
         # List of academic works
 
         # First academic work
-        self.postdoc_01 = create_postdoc(academic_work, 'postdoc_01', advisee, advisor, '2013-08-20', '2014-08-26')
+        self.postdoc_01 = create_postdoc(academic_work, 'postdoc_01', advisee, advisor, '2013-08-20', '2014-08-26',
+                                         abstract)
 
         # Second academic work
-        self.postdoc_02 = create_postdoc(academic_work, 'postdoc_02', advisee, advisor, '2013-07-01', '2014-05-26')
+        self.postdoc_02 = create_postdoc(academic_work, 'postdoc_02', advisee, advisor, '2013-07-01', '2014-05-26',
+                                         abstract)
 
         # Third academic work
-        self.postdoc_03 = create_postdoc(academic_work, 'postdoc_03', advisee, advisor, '2014-08-05', '2015-06-20')
+        self.postdoc_03 = create_postdoc(academic_work, 'postdoc_03', advisee, advisor, '2014-08-05', '2015-06-20',
[…]

### 2016-04-15 research/tests.py
NIRA-86 - Update the "Academic Work" class according to João's suggestions

@@ -31,6 +31,7 @@ def create_postdoc(type, title, advisee, advisor, start_date, end_date, abstract
     postdoc.title = title
     postdoc.advisee = advisee
     postdoc.advisor = advisor
+    postdoc.funding = False
     postdoc.start_date = start_date
     postdoc.end_date = end_date
     postdoc.abstract = abstract

### 2016-04-15 person/views.py
NIRA-83 - Create a view to generate the citation names Handling the case of a user with a defined default citation name.

@@ -93,9 +93,14 @@ def generate_citation_names(person):
 
     # Imagine a person called João Carlos da Silva.
     # Here the citation would be "Silva, JC"
-    citation_name_01 = CitationName(person_id=person_id, name=citation_01)
-    if CitationName.objects.filter(person_id=person_id, name=citation_name_01).exists() is False:
-        citation_name_01.save()
+    if citation_default:
+        citation_name_01 = CitationName(person_id=person_id, name=citation_01)
+        if CitationName.objects.filter(person_id=person_id, name=citation_name_01).exists() is False:
+            citation_name_01.save()
+    else:
+        citation_name_01 = CitationName(person_id=person_id, name=citation_01, default_name=True)
+        if CitationName.objects.filter(person_id=person_id, name=citation_name_01).exists() is False:
+            citation_name_01.save()
 
     # Here the citation would be "Silva, João Carlos"
     citation_name_02 = CitationName(person_id=person_id, name=citation_02)

### 2016-04-15 citation_name.py
citation_name script removed

@@ -1,96 +1,0 @@
-# -*- coding: utf-8 -*-
-
-# This file was created based on what is explained in:
-# https://code.djangoproject.com/wiki/InitialSQLDataDiangoORMWay
-
-from os import environ
-environ['DJANGO_SETTINGS_MODULE'] = 'sistema.settings'
-
-from person.models import Person, CitationName
-
-prep = ['da', 'do', 'de', 'dos']
-
-
-def first_letter_of_the_name():
-    letters = ''
-    for name in names:
-        if name != last_name and name not in prep:
-            letters += name[0]
-    return letters
-
-
-def names_without_last_name():
-    citation_name = [name for name in names if name != last_name and name not in prep]
-    citation_name = ' '.join(citation_name)
-    return citation_name
-
-
-def first_name_and_first_letter():
-    first_letter = ''
-    first_name = names[0]
-    for name in names:
-        if name != first_name and name != last_name and name not in prep:
-            first_letter += name[0]
-    if first_letter != '':
-        citation_name = first_name+' '+first_letter
-        return citation_name
-    else:
-        citation_name = first_name
-        return citation_name
-
-
-# Create the citation name for each person
-for person in Person.objects.all():
-    # Get full name and id from person.
-    full_name = person.full_name
-    person_id = person.pk
-
-    # Split the full name.
-    names = full_name.split()
-
-    # Get the last name
-    last_name = names[-1]
-
-    # Get the first letter of the name except the last name
-    letters = first_letter_of_the_name()
-
-    # Get names without last name
-    almost_full_name = names_without_last_name()
-
-    # Get first name and first letter of the middle name
-    first_name_letter_middle_name = first_name_and_first_letter()
-
-    # Imagine a person called João Carlos da Silva.
-    # Here the citation would be "Silva, JC"
-    citation_name_01 = CitationName(person_id=person_id, name=last_name+','+' '+letters)
-    if CitationName.objects.filter(person_id=person_id, name=citation_name_01).exists() is False:
-        citation_name_01.save()
-
-    # Here the citation would be "Silva, João Carlos"
-    citation_name_02 = CitationName(person_id=person_id, name=last_name+','+' '+almost_full_name)
-    if CitationName.objects.filter(person_id=person_id, name=citation_name_02).exists() is False:
-        citation_name_02.save()
-
-    # Here the citation would be "Silva, João C"
[…]

### 2016-04-15 person/tests.py
NIRA-83 - Create a view to generate the citation names Wrote unit tests for the citation names generator.

@@ -1,6 +1,12 @@
+# -*- coding: utf-8 -*-
+from django.core.urlresolvers import reverse
 from django.test import TestCase
+from person.models import Person, CitationName
+from person.views import name_with_first_letters, names_without_last_name, first_name_and_first_letter, \
+    generate_citation_names
 from validation import CPF
 
+prep = ['e', 'da', 'do', 'de', 'dos', 'E', 'Da', 'Do', 'De', 'Dos']
 
 class CpfValidationTest(TestCase):
     """
@@ -97,3 +103,58 @@ class CpfValidationTest(TestCase):
             '1234567890123456789012345678901234567890123456789012\
             34567890123456789012345678901234567890123456789012345678901234567890').isValid()
         self.assertEqual(result, False)
+
+
+class CitationsTest(TestCase):
+
+    def setUp(self):
+        self.person1 = Person(full_name='João Carlos da Silva')
+        self.person1.save()
+
+        self.person2 = Person(full_name='Antonio da Silva')
+        self.person2.save()
+
+        self.person1_id = self.person1.pk
+        self.person2_id = self.person2.pk
+
+        citation2 = CitationName(person_id=self.person2_id, name='da Silva, A', default_name=True)
+        citation2.save()
+
+    def test_name_with_first_letters(self):
+
+        result = name_with_first_letters(self.person1.full_name.split(), False)
+        self.assertEqual(result, 'Silva, JC')
+
+        result = name_with_first_letters(self.person1.full_name.split(), True)
+        self.assertEqual(result, 'da Silva, JC')
+
+    def test_names_without_last_name(self):
+
+        result = names_without_last_name(self.person1.full_name.split(), False)
+        self.assertEqual(result, 'Silva, João Carlos')
+
+        result = names_without_last_name(self.person1.full_name.split(), True)
+        self.assertEqual(result, 'da Silva, João Carlos')
+
+    def test_first_name_and_first_letter(self):
+
+        result = first_name_and_first_letter(self.person1.full_name.split(), False)
+        self.assertEqual(result,'Silva, João C')
+
+        result = first_name_and_first_letter(self.person1.full_name.split(), True)
+        self.assertEqual(result,'da Silva, João C')
+
+    def test_generate_citation_names(self):
+
+        for person in Person.objects.all():
+            generate_citation_names(person)
+
+        citation = CitationName.objects.filter(person_id=self.person1_id, default_name=True)
[…]

### 2016-04-15 person/views.py

@@ -73,9 +73,6 @@ def generate_citation_names(person):
     # Split the full name.
     split_name = full_name.split()
 
-    # Get the last name
-    last_name = split_name[-1]
-
     # Maybe the user has a default citation
     citation_default = CitationName.objects.filter(person_id=person_id, default_name=True)
 

### 2016-04-26 research/views.py
NIRA-92 - Fix the link to the article in the latex report

@@ -167,6 +167,30 @@ def articles(request):
     return render(request, 'report/research/articles.html')
 
 
+def tex_escape(response):
+    """
+        :param text: a plain text message
+        :return: the message escaped to appear correctly in LaTeX
+    """
+    conv = {
+        '{ ': '{',
+        ' }': '}',
+        '&': r'\&',
+        '%': r'\%',
+        '$': r'\$',
+        '#': r'\#',
+        '_': r'\_',
+        '<': r'\textless',
+        '>': r'\textgreater',
+    }
+
+    for key in conv:
+        if key in response:
+            response = re.sub(key, conv[key], response)
+
+    return response
+
+
 @login_required
 def articles_tex(request):
     start_date = request.GET.get('start_date')
@@ -191,10 +215,12 @@ def articles_tex(request):
                'published_tec_trans_in_event': published_tec_trans_in_event,
                'accepted_tec_trans_in_event': accepted_tec_trans_in_event}
 
-    response = HttpResponse(render_to_string('report/research/tex/articles.tex', context),
-                            content_type='text/plain')
-    response['Content-Disposition'] = 'attachment; filename="articles.tex"'
-    return response
+    response = render_to_string('report/research/tex/articles.tex', context)
+    response = tex_escape(response)
+    latex_response = HttpResponse(response, content_type='text/plain')
+    latex_response['Content-Disposition'] = 'attachment; filename="articles.tex"'
+
+    return latex_response
 
 
 def search_academic_works(start_date, end_date):

### 2016-04-27 research/views.py
NIRA-92 - Fix the link to the article in the latex report

@@ -169,7 +169,7 @@ def articles(request):
 
 def tex_escape(response):
     """
-        :param text: a plain text message
+        :param: a plain text message
         :return: the message escaped to appear correctly in LaTeX
     """
     conv = {

### 2016-04-27 dissemination/tests.py
NIRA-88 - Create different reports to show the internal production from the dissemination team Unit test for the dissemination_report view.

@@ -1,71 +1,94 @@
 # -*- coding: utf-8 -*-
-from dissemination.views import dissemination_report
+from dissemination.models import InternalMediaOutlet, Internal, ExternalMediaOutlet, External
 from research.tests import system_authentication
 from django.core.urlresolvers import reverse
-from django.test import TestCase, RequestFactory
+from django.test import TestCase
 
 
 class DisseminationTest(TestCase):
 
+    """
+    The following tests are performed:
+    1 - Dissemination report for external with date;
+    2 - Dissemination report for external without date;
+    3 - Dissemination report for internal with date;
+    4 - Dissemination report for internal without date;
+    5 - Dissemination report without type selected.
+    """
+
     def setUp(self):
+
         logged, self.user, self.factory = system_authentication(self)
         self.assertEqual(logged, True)
 
-    def test_without_type(self):
-        response = self.client.get(reverse('dissemination_report'))
-        self.assertEqual(response.status_code, 200)
+        internal_media_1 = InternalMediaOutlet(name="Blog")
+        internal_media_1.save()
+
+        internal_media_2 = InternalMediaOutlet(name="Newsletter")
+        internal_media_2.save()
+
+        dissemination1 = Internal(title='Hello, blog!', date='2015-01-01', media_outlet=internal_media_1)
+        dissemination1.save()
+
+        dissemination2 = Internal(title='Hello, newsletter!', date='2015-01-02', media_outlet=internal_media_2)
+        dissemination2.save()
+
+        external_media = ExternalMediaOutlet(name='External Blog')
+        external_media.save()
+
+        dissemination3 = External(title='Hello, external blog!', date='2015-01-03', media_outlet=external_media)
+        dissemination3.save()
 
     def test_dissemination_report_without_date (self):
 
         # With type external selected
-        request = self.factory.post(reverse('dissemination_report'), {'type': 'e',
-                                                                      'start_date': '',
-                                                                      'end_date': ''})
-        request.user = self.user
-        response = dissemination_report(request)
+        response = self.client.post(reverse('dissemination_report'), {'type': 'e',
+                                                                     'start_date': '',
+                                                                     'end_date': ''})
+        cont = response.context['disseminations']
+        self.assertEqual(len(cont), 1)
         self.assertEqual(response.status_code, 200)
 
         # With type internal selected
-        request = self.factory.post(reverse('dissemination_report'), {'type': 'i',
-                                                                      'internal_type': 1,
-                                                                      'start_date': '',
[…]

### 2016-04-27 static/js/dissemination.js
Fixed a javascript file.

@@ -7,6 +7,14 @@ $(document).ready(function () {
     var $id_type = $('#id_type');
 
     // ### Hide or show internal class field ###
+    $id_type.each(function() {
+        if($(this).val() == 'i'){
+           $("#id_class_internal_field").show();
+       } else {
+           $("#id_class_internal_field").hide();
+       }
+    });
+
     $id_type.on('change', (function () {
        if($(this).val() == 'i'){
            $("#id_class_internal_field").show();
@@ -15,6 +23,4 @@ $(document).ready(function () {
        }
     }));
 });
-
-
 

### 2016-04-27 templates/report/research/tex/articles.tex

--- 2016-04-04 templates/report/research/tex/articles.tex
@@
 {% if published_scientific or accepted_scientific or submitted_scientific or draft_scientific or published_dissemin or accepted_dissemin or submitted_dissemin or draft_dissemin or published_tec_trans or accepted_tec_trans or submitted_tec_trans or draft_tec_trans or published_scientific_in_event or accepted_scientific_in_event or published_dissemin_in_event or accepted_dissemin_in_event or published_tec_trans_in_event or accepted_tec_trans_in_event%}
-
 	{% if published_scientific or accepted_scientific %}
-\subsubsection{Published or accepted}
+\paragraph{Published or Accepted}
 \begin{enumerate}
@@
 			{% for article in published_scientific %}
-				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %}{{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %} {{ article.article.authors }}.
-{{ article.article.periodical }},{% endif %}{% if article.volume %}\textbf{ {{ article.volume }} }{% endif %}{% if article.number %} ({{ article.number }}),{% endif %}{% if article.start_page and article.end_page %} {{ article.start_page }}-{{ article.end_page }},{% endif %} {% if article.doi %}DOI: {{ article.doi }},{% endif %} {{ article.date|date:"Y" }}.{% endif %}
+				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %}  \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} } {{ article.article.periodical }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.periodical }},{% endif %} {% if article.volume %}\textbf{ {{ article.volume }} }{% endif %}{% if article.number %} ({{ article.number }}),{% endif %}{% if article.start_page and article.end_page %} {{ article.start_page }}-{{ article.end_page }},{% endif %} {% if article.doi %}DOI: {{ article.doi }},{% endif %} {{ article.date|date:"Y" }}.{% endif %}
 			{% endfor %}
@@
 			{% for article in accepted_scientific %}
-				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %}{{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %} {{ article.article.authors }}.
-{{ article.article.periodical }},{% endif %} {{ article.date|date:"Y" }}, to appear.{% endif %}
+				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} } {{ article.article.periodical }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.periodical }},{% endif %} {{ article.date|date:"Y" }}, to appear.{% endif %}
 			{% endfor %}
 		{% endif %}
-\end{enumerate}
 	{% endif %}
@@
 	{% if published_dissemin or accepted_dissemin %}
-\subsubsection{Published or accepted from the dissemination team}
-\begin{enumerate}
+\vspace{0.5cm}
+\hspace{-1cm}\noindent{\bf Published or accepted from the dissemination team}
 		{% if published_dissemin %}
 			{% for article in published_dissemin %}
-				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %}{{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %} {{ article.article.authors }}.
-{{ article.article.periodical }},{% endif %}{% if article.volume %}\textbf{ {{ article.volume }} }{% endif %}{% if article.number %} ({{ article.number }}),{% endif %}{% if article.start_page and article.end_page %} {{ article.start_page }}-{{ article.end_page }},{% endif %} {% if article.doi %}DOI: {{ article.doi }},{% endif %} {{ article.date|date:"Y" }}.{% endif %}
+				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} } {{ article.article.periodical }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.periodical }},{% endif %} {% if article.volume %}\textbf{ {{ article.volume }} }{% endif %}{% if article.number %} ({{ article.number }}),{% endif %}{% if article.start_page and article.end_page %} {{ article.start_page }}-{{ article.end_page }},{% endif %} {% if article.doi %}DOI: {{ article.doi }},{% endif %} {{ article.date|date:"Y" }}.{% endif %}
 			{% endfor %}
@@
 		{% if accepted_dissemin %}
-			{% for article in accepted_scientific %}
-				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %}{{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %} {{ article.article.authors }}.
-{{ article.article.periodical }},{% endif %} {{ article.date|date:"Y" }}, to appear.{% endif %}
+			{% for article in accepted_dissemin %}
+				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} } {{ article.article.periodical }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.periodical }},{% endif %} {{ article.date|date:"Y" }}, to appear.{% endif %}
 			{% endfor %}
 		{% endif %}
-\end{enumerate}
 	{% endif %}
@@
 	{% if published_tec_trans or accepted_tec_trans %}
-\subsubsection{Published or accepted from the technological transfer team}
-\begin{enumerate}
+\vspace{0.5cm}
+\hspace{-1cm}\noindent{\bf Published or accepted from the technological transfer team}
 		{% if published_tec_trans %}
 			{% for article in published_tec_trans %}
-				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %}{{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %} {{ article.article.authors }}.
-{{ article.article.periodical }},{% endif %}{% if article.volume %}\textbf{ {{ article.volume }} }{% endif %}{% if article.number %} ({{ article.number }}),{% endif %}{% if article.start_page and article.end_page %} {{ article.start_page }}-{{ article.end_page }},{% endif %} {% if article.doi %}DOI: {{ article.doi }},{% endif %} {{ article.date|date:"Y" }}.{% endif %}
+				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} } {{ article.article.periodical }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.periodical }},{% endif %} {% if article.volume %}\textbf{ {{ article.volume }} }{% endif %}{% if article.number %} ({{ article.number }}),{% endif %}{% if article.start_page and article.end_page %} {{ article.start_page }}-{{ article.end_page }},{% endif %} {% if article.doi %}DOI: {{ article.doi }},{% endif %} {{ article.date|date:"Y" }}.{% endif %}
 			{% endfor %}
@@
 			{% for article in accepted_tec_trans %}
-				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %}{{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %} {{ article.article.authors }}.
-{{ article.article.periodical }},{% endif %} {{ article.date|date:"Y" }}, to appear.{% endif %}
+				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} } {{ article.article.periodical }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.periodical }},{% endif %} {{ article.date|date:"Y" }}, to appear.{% endif %}
+			{% endfor %}
+		{% endif %}
+	{% endif %}
+
+	{% if submitted_scientific %}
+\vspace{0.5cm}
+\hspace{-1cm}\noindent{\bf Submitted}
+		{% for article in submitted_scientific %}
+			{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{% else %}\textit{ {{ article.article.authors }}.}{% endif %}{% endif %}
+		{% endfor %}
+	{% endif %}
+
+	{% if submitted_dissemin %}
+\vspace{0.5cm}
+\hspace{-1cm}\noindent{\bf Submitted from the dissemination team}
+		{% for article in submitted_dissemin %}
+			{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{% else %}\textit{ {{ article.article.authors }}.}{% endif %}{% endif %}
+		{% endfor %}
+	{% endif %}
+
+	{% if submitted_tec_trans %}
+\vspace{0.5cm}
+\hspace{-1cm}\noindent{\bf Submitted from the technological transfer team}
+		{% for article in submitted_tec_trans %}
+			{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{% else %}\textit{ {{ article.article.authors }}.}{% endif %}{% endif %}
+		{% endfor %}
+	{% endif %}
+
+	{% if published_scientific_in_event or accepted_scientific_in_event %}
+\vspace{0.5cm}
+\hspace{-1cm}\noindent{\bf Communications in meetings with referee}
+		{% if published_scientific_in_event %}
+			{% for article in published_scientific_in_event %}
+				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} } {{ article.article.event }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.event }},{% endif %}{% if article.article.event.acronym %} {{ article.article.event.acronym }}{% endif %}, {{ article.article.event.local }}, {% if article.article.event.start_date|date:"M" == article.article.event.end_date|date:"M" %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"d, Y" }}{% else %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"M d, Y" }}.{% endif %}{% endif %}
+			{% endfor %}
+		{% endif %}
+		{% if accepted_scientific_in_event %}
+			{% for article in published_scientific_in_event %}
+				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} } {{ article.article.event }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.event }},{% endif %}{% if article.article.event.acronym %} {{ article.article.event.acronym }}{% endif %}, {{ article.article.event.local }}, {% if article.article.event.start_date|date:"M" == article.article.event.end_date|date:"M" %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"d, Y" }}, to be held{% else %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"M d, Y" }}, to be held{% endif %}.{% endif %}
+			{% endfor %}
+		{% endif %}
+	{% endif %}
+
+	{% if published_dissemin_in_event or accepted_dissemin_in_event %}
+\vspace{0.5cm}
+\hspace{-1cm}\noindent{\bf Communications in meetings with referee from the dissemination team}
+		{% if published_dissemin_in_event %}
+			{% for article in published_dissemin_in_event %}
+				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} } {{ article.article.event }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.event }},{% endif %}{% if article.article.event.acronym %} {{ article.article.event.acronym }}{% endif %}, {{ article.article.event.local }}, {% if article.article.event.start_date|date:"M" == article.article.event.end_date|date:"M" %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"d, Y" }}{% else %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"M d, Y" }}.{% endif %}{% endif %}
+			{% endfor %}
+		{% endif %}
+		{% if accepted_dissemin_in_event %}
+			{% for article in accepted_dissemin_in_event %}
+				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} } {{ article.article.event }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.event }},{% endif %}{% if article.article.event.acronym %} {{ article.article.event.acronym }}{% endif %}, {{ article.article.event.local }}, {% if article.article.event.start_date|date:"M" == article.article.event.end_date|date:"M" %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"d, Y" }}, to be held{% else %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"M d, Y" }}, to be held{% endif %}.{% endif %}
+			{% endfor %}
+		{% endif %}
+	{% endif %}
+
+	{% if published_tec_trans_in_event or accepted_tec_trans_in_event %}
+\vspace{0.5cm}
+\hspace{-1cm}\noindent{\bf Communications in meetings with referee from the technological transfer team}
+		{% if published_tec_trans_in_event %}
+			{% for article in published_tec_trans_in_event %}
+				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} } {{ article.article.event }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.event }},{% endif %}{% if article.article.event.acronym %} {{ article.article.event.acronym }}{% endif %}, {{ article.article.event.local }}, {% if article.article.event.start_date|date:"M" == article.article.event.end_date|date:"M" %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"d, Y" }}{% else %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"M d, Y" }}.{% endif %}{% endif %}
+			{% endfor %}
+		{% endif %}
+		{% if accepted_tec_trans_in_event %}
+			{% for article in accepted_tec_trans_in_event %}
+				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} } {{ article.article.event }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.event }},{% endif %}{% if article.article.event.acronym %} {{ article.article.event.acronym }}{% endif %}, {{ article.article.event.local }}, {% if article.article.event.start_date|date:"M" == article.article.event.end_date|date:"M" %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"d, Y" }}, to be held{% else %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"M d, Y" }}, to be held{% endif %}.{% endif %}
+			{% endfor %}
+		{% endif %}
+	{% endif %}
+
+	{% if draft_scientific %}
+\vspace{0.5cm}
+\hspace{-1cm}\noindent{\bf Drafts}
+		{% for article in draft_scientific %}
+			{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{% else %}\textit{ {{ article.article.authors }}.}{% endif %}{% endif %}
+		{% endfor %}
+	{% endif %}
+
+	{% if draft_dissemin %}
+\vspace{0.5cm}
+\hspace{-1cm}\noindent{\bf Drafts from the dissemination team}
+		{% for article in draft_dissemin %}
+			{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{% else %}\textit{ {{ article.article.authors }}.}{% endif %}{% endif %}
+		{% endfor %}
+	{% endif %}
+
+	{% if draft_tec_trans %}
+\vspace{0.5cm}
+\hspace{-1cm}\noindent{\bf Drafts from the technological transfer team}
+		{% for article in draft_tec_trans %}
+			{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{% else %}\textit{ {{ article.article.authors }}.}{% endif %}{% endif %}
 		{% endfor %}
@@
 \end{enumerate}
-	{% endif %}
 

### 2016-04-27 dissemination/tests.py
NIRA-88 - Create different reports to show the internal production from the dissemination team Now with full test coverage.

@@ -13,7 +13,8 @@ class DisseminationTest(TestCase):
     2 - Dissemination report for external without date;
     3 - Dissemination report for internal with date;
     4 - Dissemination report for internal without date;
-    5 - Dissemination report without type selected.
+    5 - Dissemination report without type selected;
+    6 - Dissemination report with invalid dates selected.
     """
 
     def setUp(self):
@@ -91,4 +92,11 @@ class DisseminationTest(TestCase):
 
     def test_without_type(self):
         response = self.client.get(reverse('dissemination_report'))
+        self.assertEqual(response.status_code, 200)
+
+    def test_dissemination_report_invalid_dates(self):
+        # With type external selected
+        response = self.client.post(reverse('dissemination_report'), {'type': 'e',
+                                                                      'start_date': '01-01-2019',
+                                                                      'end_date': '01-02-2017'})
         self.assertEqual(response.status_code, 200)

### 2016-05-02 dissemination/views.py
NIRA-93 - Generate latex for the dissemination report If the user chooses an internal dissemination, the table has a caption with the chosen internal media outlet.

@@ -65,13 +65,15 @@ def dissemination_report(request):
             internal_type = request.POST['internal_type']
             disseminations = Internal.objects.filter(media_outlet_id=internal_type, date__gt=start_date,
                                                      date__lt=end_date).order_by('-date')
+            media_name = InternalMediaOutlet.objects.get(id=internal_type).name
 
         else:
             disseminations = Dissemination.objects.filter(type_of_media='e', date__gt=start_date,
                                                           date__lt=end_date).order_by('-date')
+            media_name = ''
 
         if end_date >= start_date:
-            context = {'disseminations': disseminations, 'type': type}
+            context = {'disseminations': disseminations, 'type': type, 'media_name': media_name}
             return render(request, 'report/dissemination/dissemination_report.html', context)
         else:
             context = {'types': types, 'internal_types': internal_types}

### 2016-05-02 templates/report/dissemination/tex/disseminations.tex
NIRA-93 - Generate latex for the dissemination report If the user chooses an internal dissemination, the table has a caption with the chosen internal media outlet.

{% autoescape off %}
{% block content %}

{% if type == 'i' %}
    \begin{longtable}{ |p{4cm}|p{4cm}|p{5cm}|p{2cm}| }
    Title & Topics & URL & Date \\
    \hline
    {% for dissemination in disseminations %}
        {{ dissemination.title }} & {{ dissemination.topics }} & {{ dissemination.link }} & {{ dissemination.date|date:"M d, Y" }} \\
    \hline
    {% endfor %}
    \end{longtable}

{% elif type == 'e' %}
    \begin{longtable}{ |p{3cm}|p{2,3cm}|p{2cm}|p{3cm}|p{3,5cm}|p{1,2cm}| }
    \hline
    \textbf{Title} & \textbf{Authors} & Media outlet & Topics & URL & Date \\
    \hline
    {% for dissemination in disseminations %}
        {{ dissemination.title }} & {{ dissemination.external.authors }} & {{ dissemination.external.media_outlet }} & {{ dissemination.topics }} & {{ dissemination.link }}&#125; & {{ dissemination.date|date:"M d, Y" }} \\
    \hline
    {% endfor %}
    \end{longtable}
{% endif %}

{% endblock %}
{% endautoescape %}

### 2016-05-02 dissemination/urls.py

@@ -4,4 +4,5 @@ from dissemination import views
 
 urlpatterns = patterns('',
     url(r'^dissemination_report/$', views.dissemination_report, name='dissemination_report'),
+    url(r'^dissemination_tex/$', views.dissemination_tex, name='dissemination_tex'),
 )

### 2016-05-02 dissemination/views.py

@@ -1,10 +1,12 @@
 # -*- coding: utf-8 -*-
 from helper_functions.date import *
-from django.shortcuts import render
+from helper_functions.latex import *
+from dissemination.models import Dissemination, Internal, InternalMediaOutlet, TYPE_OF_MEDIA
+from django.shortcuts import render, HttpResponse
 from django.contrib import messages
 from django.contrib.auth.decorators import login_required
-from dissemination.models import Dissemination, Internal, InternalMediaOutlet, TYPE_OF_MEDIA
 from django.utils.translation import ugettext_lazy as _
+from django.template.loader import render_to_string
 
 
 @login_required
@@ -13,6 +15,7 @@ def dissemination_report(request):
     types = [{'value': type[0], 'display': type[1].encode('utf-8')} for type in TYPE_OF_MEDIA]
     internal_types = InternalMediaOutlet.objects.all()
     internal_types = [{'value': type.id, 'display': type.name} for type in internal_types]
+    internal_type = ''
 
     if request.method == 'POST':
 
@@ -34,17 +37,20 @@ def dissemination_report(request):
 
         if type == 'i':
             internal_type = request.POST['internal_type']
-            disseminations = Internal.objects.filter(media_outlet_id=internal_type, date__gt=start_date,
-                                                     date__lt=end_date).order_by('-date')
+            disseminations = internal_filter(internal_type, start_date, end_date)
             media_name = InternalMediaOutlet.objects.get(id=internal_type).name
 
         else:
-            disseminations = Dissemination.objects.filter(type_of_media='e', date__gt=start_date,
-                                                          date__lt=end_date).order_by('-date')
+            disseminations = external_filter(start_date, end_date)
             media_name = ''
 
         if end_date >= start_date:
-            context = {'disseminations': disseminations, 'type': type, 'media_name': media_name}
+            context = {'start_date': start_date,
+                       'end_date': end_date,
+                       'disseminations': disseminations,
+                       'type': type,
+                       'media_name': media_name,
+                       'internal_type': internal_type}
             return render(request, 'report/dissemination/dissemination_report.html', context)
         else:
             context = {'types': types, 'internal_types': internal_types}
@@ -54,3 +60,39 @@ def dissemination_report(request):
     context = {'types': types, 'internal_types': internal_types}
 
     return render(request, 'report/dissemination/dissemination.html', context)
+
+
+def dissemination_tex(request):
+
+    start_date = request.GET.get('start_date')
[…]

### 2016-05-03 dissemination/admin.py
Actions: (1) PEP8 corrections. (2) Author is not mandatory. (3) Not using tex_escape def

@@ -1,7 +1,6 @@
 from django.contrib import admin
 from dissemination.models import *
 from dissemination.forms import *
-from django.utils.translation import ugettext_lazy as _
 
 admin.site.register(Topic)
 admin.site.register(InternalMediaOutlet)

### 2016-05-03 dissemination/models.py

@@ -78,8 +78,7 @@ class Internal(Dissemination):
     'authors'           Get the authors of the publication.
     """
     media_outlet = models.ForeignKey(InternalMediaOutlet, verbose_name=_('Media outlet'))
-    author = models.ManyToManyField(Person, verbose_name=_('Author'), blank=True, null=True,
-                                    limit_choices_to={'role__name': 'Journalist'})
+    author = models.ManyToManyField(Person, verbose_name=_('Author'), blank=True, null=True)
 
     class Meta:
         verbose_name = _('Internal')
@@ -120,7 +119,7 @@ class External(Dissemination):
     'authors'           Get the authors of the publication.
     """
     media_outlet = models.ForeignKey(ExternalMediaOutlet, verbose_name=_('Media outlet'))
-    author = models.ManyToManyField(Person, verbose_name=_('Author'), limit_choices_to={'role__name': 'Journalist'})
+    author = models.ManyToManyField(Person, verbose_name=_('Author'), blank=True, null=True)
 
     class Meta:
         verbose_name = _('External')

### 2016-05-03 dissemination/tests.py

@@ -40,22 +40,20 @@ class DisseminationTest(TestCase):
         dissemination3 = External(title='Hello, external blog!', date='2015-01-03', media_outlet=external_media)
         dissemination3.save()
 
-    def test_dissemination_report_without_date (self):
+    def test_dissemination_report_without_date(self):
 
         # With type external selected
-        response = self.client.post(reverse('dissemination_report'), {'type': 'e',
-                                                                     'start_date': '',
-                                                                     'end_date': ''})
+        response = self.client.post(reverse('dissemination_report'), {'type': 'e', 'start_date': '', 'end_date': ''})
         cont = response.context['disseminations']
         self.assertEqual(len(cont), 1)
         self.assertEqual(response.status_code, 200)
 
         # With type internal selected
         internal_types = InternalMediaOutlet.objects.all()
-        internal_types = [{'value': type.id, 'display': type.name} for type in internal_types]
+        internal_types = [{'value': media.id, 'display': media.name} for media in internal_types]
 
-        for type in internal_types:
-            value = type['value']
+        for media in internal_types:
+            value = media['value']
             response = self.client.post(reverse('dissemination_report'), {'type': 'i',
                                                                           'internal_type': value,
                                                                           'start_date': '',
@@ -66,7 +64,7 @@ class DisseminationTest(TestCase):
 
         self.assertEqual(response.status_code, 200)
 
-    def test_dissemination_report_with_date (self):
+    def test_dissemination_report_with_date(self):
 
         # With type external selected
         response = self.client.post(reverse('dissemination_report'), {'type': 'e',
@@ -78,10 +76,10 @@ class DisseminationTest(TestCase):
 
         # With type internal selected
         internal_types = InternalMediaOutlet.objects.all()
-        internal_types = [{'value': type.id, 'display': type.name} for type in internal_types]
+        internal_types = [{'value': media.id, 'display': media.name} for media in internal_types]
 
-        for type in internal_types:
-            value = type['value']
+        for media in internal_types:
+            value = media['value']
             response = self.client.post(reverse('dissemination_report'), {'type': 'i',
                                                                           'internal_type': value,
                                                                           'start_date': '01-01-2015',

### 2016-05-03 dissemination/views.py

@@ -1,20 +1,31 @@
 # -*- coding: utf-8 -*-
 from helper_functions.date import *
-from helper_functions.latex import *
 from dissemination.models import Dissemination, Internal, InternalMediaOutlet, TYPE_OF_MEDIA
-from django.shortcuts import render, HttpResponse
 from django.contrib import messages
 from django.contrib.auth.decorators import login_required
-from django.utils.translation import ugettext_lazy as _
+from django.shortcuts import render, HttpResponse
 from django.template.loader import render_to_string
+from django.utils.translation import ugettext_lazy as _
+
+
+def internal_filter(internal_type, start_date, end_date):
+    disseminations = Internal.objects.filter(media_outlet_id=internal_type, date__gt=start_date,
+                                             date__lt=end_date).order_by('-date')
+    return disseminations
+
+
+def external_filter(start_date, end_date):
+    disseminations = Dissemination.objects.filter(type_of_media='e', date__gt=start_date,
+                                                  date__lt=end_date).order_by('-date')
+    return disseminations
 
 
 @login_required
 def dissemination_report(request):
 
-    types = [{'value': type[0], 'display': type[1].encode('utf-8')} for type in TYPE_OF_MEDIA]
+    types = [{'value': media_type[0], 'display': media_type[1].encode('utf-8')} for media_type in TYPE_OF_MEDIA]
     internal_types = InternalMediaOutlet.objects.all()
-    internal_types = [{'value': type.id, 'display': type.name} for type in internal_types]
+    internal_types = [{'value': media.id, 'display': media.name} for media in internal_types]
     internal_type = ''
 
     if request.method == 'POST':
@@ -33,9 +44,9 @@ def dissemination_report(request):
         else:
             end_date = now_plus_thirty()
 
-        type = request.POST['type']
+        media_type = request.POST['type']
 
-        if type == 'i':
+        if media_type == 'i':
             internal_type = request.POST['internal_type']
             disseminations = internal_filter(internal_type, start_date, end_date)
             media_name = InternalMediaOutlet.objects.get(id=internal_type).name
@@ -48,7 +59,7 @@ def dissemination_report(request):
             context = {'start_date': start_date,
                        'end_date': end_date,
                        'disseminations': disseminations,
-                       'type': type,
+                       'type': media_type,
                        'media_name': media_name,
                        'internal_type': internal_type}
             return render(request, 'report/dissemination/dissemination_report.html', context)
[…]

### 2016-05-03 dissemination/migrations/0002_auto_20160503_1037.py
Actions: (1) PEP8 corrections. (2) Author is not mandatory. (3) Not using tex_escape def

@@ -1,0 +1,20 @@
+# -*- coding: utf-8 -*-
+from __future__ import unicode_literals
+
+from django.db import models, migrations
+
+
+class Migration(migrations.Migration):
+
+    dependencies = [
+        ('dissemination', '0001_initial'),
+    ]
+
+    operations = [
+        migrations.AlterField(
+            model_name='external',
+            name='author',
+            field=models.ManyToManyField(to='person.Person', null=True, verbose_name='Author', blank=True),
+            preserve_default=True,
+        ),
+    ]

### 2016-05-03 scientific_mission/admin.py
NIRA-71 - Create an app called "Scientific missions" to store info about daily stipend.

@@ -1,0 +1,15 @@
+from scientific_mission.models import *
+from scientific_mission.forms import *
+from django.contrib import admin
+
+
+admin.site.register(Type)
+
+
+class ScientificMissionAdmin(admin.ModelAdmin):
+    fields = ['person', 'mission', 'project_activity', 'origin_country', 'origin_city', 'destination_country',
+              'destination_city', 'departure', 'arrival', 'value']
+    list_display = ('person', 'mission', 'destination_city', 'departure', 'arrival', 'value')
+    list_display_links = ('person',)
+    form = ScientificMissionForm
+admin.site.register(ScientificMission, ScientificMissionAdmin)

### 2016-05-03 scientific_mission/forms.py

@@ -1,0 +1,22 @@
+from scientific_mission.models import ScientificMission
+from cities_light.models import Country, City
+from django import forms
+from django.forms import Select
+from django.utils.translation import ugettext_lazy as _
+
+
+class ScientificMissionForm(forms.ModelForm):
+
+    origin_country = forms.ModelChoiceField(Country.objects.all(), label=_('Country of origin'), initial=31,
+                                            widget=Select(attrs={'onchange': 'load_origin_cities(this.value);'}))
+    origin_city = forms.ModelChoiceField(City.objects.filter(country_id=31), label=_('City of origin'))
+    destination_country = forms.ModelChoiceField(Country.objects.all(), label=_('Country of destination'), initial=31,
+                                                 widget=Select(attrs={'onchange': 'load_destination_cities(this.value);'}))
+    destination_city = forms.ModelChoiceField(City.objects.filter(country_id=31), label=_('City of destination'),
+                                              initial=1383)
+
+    class Meta:
+        model = ScientificMission
+
+    class Media:
+        js = ('/static/js/load_cities.js',)

### 2016-05-03 scientific_mission/migrations/0001_initial.py

@@ -1,0 +1,76 @@
+# -*- coding: utf-8 -*-
+from __future__ import unicode_literals
+
+from django.db import models, migrations
+
+
+class Migration(migrations.Migration):
+
+    dependencies = [
+        ('activity', '0001_initial'),
+        ('cities_light', '0006_compensate_for_0003_bytestring_bug'),
+        ('person', '0003_remove_person_citation_name'),
+    ]
+
+    operations = [
+        migrations.CreateModel(
+            name='ScientificMission',
+            fields=[
+                ('id', models.AutoField(verbose_name='ID', serialize=False, auto_created=True, primary_key=True)),
+                ('departure', models.DateTimeField(verbose_name='Departure')),
+                ('arrival', models.DateTimeField(verbose_name='Arrival')),
+                ('value', models.CharField(max_length=50, null=True, verbose_name='Value', blank=True)),
+                ('destination_city', models.ForeignKey(related_name='destination_city', verbose_name='City of destination', to='cities_light.City')),
+                ('destination_country', models.ForeignKey(related_name='destination_country', verbose_name='Country of destination', to='cities_light.Country')),
+            ],
+            options={
+                'ordering': ('person',),
+                'verbose_name': 'Daily stipend',
+                'verbose_name_plural': 'Daily stipends',
+            },
+            bases=(models.Model,),
+        ),
+        migrations.CreateModel(
+            name='Type',
+            fields=[
+                ('id', models.AutoField(verbose_name='ID', serialize=False, auto_created=True, primary_key=True)),
+                ('mission', models.CharField(max_length=255, null=True, verbose_name='Scientific Mission', blank=True)),
+            ],
+            options={
+                'ordering': ('mission',),
+                'verbose_name': 'Type of scientific mission',
+                'verbose_name_plural': 'Types of scientific mission',
+            },
+            bases=(models.Model,),
+        ),
+        migrations.AddField(
+            model_name='scientificmission',
+            name='mission',
+            field=models.ForeignKey(verbose_name='Mission', blank=True, to='scientific_mission.Type', null=True),
+            preserve_default=True,
+        ),
+        migrations.AddField(
+            model_name='scientificmission',
+            name='origin_city',
+            field=models.ForeignKey(verbose_name='City of origin', to='cities_light.City'),
+            preserve_default=True,
+        ),
+        migrations.AddField(
+            model_name='scientificmission',
+            name='origin_country',
[…]

### 2016-05-03 scientific_mission/models.py

@@ -1,0 +1,49 @@
+from activity.models import ProjectActivities
+from cities_light.models import City, Country, Region
+from person.models import Person
+from django.db import models
+from django.utils.translation import ugettext_lazy as _
+
+
+class Type(models.Model):
+    """
+    An instance of this class is a type of scientific mission.
+
+    '__unicode__'		Returns the mission.
+    'class Meta'		Sets the description (singular and plural) model and the ordering of data by mission.
+    """
+    mission = models.CharField(_('Scientific Mission'), max_length=255, blank=True, null=True)
+
+    def __unicode__(self):
+        return u'%s' % self.mission
+
+    class Meta:
+        verbose_name = _('Type of scientific mission')
+        verbose_name_plural = _('Types of scientific mission')
+        ordering = ('mission', )
+
+
+class ScientificMission(models.Model):
+    """
+    An instance of this class is a daily stipend paid to a person.
+
+    """
+    person = models.ForeignKey(Person, verbose_name=_('Paid to'))
+    mission = models.ForeignKey(Type, verbose_name=_('Mission'), blank=True, null=True)
+    project_activity = models.ForeignKey(ProjectActivities, verbose_name=_('Project activity'), blank=True, null=True)
+    origin_country = models.ForeignKey(Country, verbose_name=_('Country of origin'))
+    origin_city = models.ForeignKey(City, verbose_name=_('City of origin'))
+    destination_country = models.ForeignKey(Country, verbose_name=_('Country of destination'),
+                                            related_name='destination_country')
+    destination_city = models.ForeignKey(City, verbose_name=_('City of destination'), related_name='destination_city')
+    departure = models.DateTimeField(_('Departure'))
+    arrival = models.DateTimeField(_('Arrival'))
+    value = models.CharField(_('Value'), max_length=50, blank=True, null=True)
+
+    def __unicode__(self):
+        return u'%s' % self.person
+
+    class Meta:
+        verbose_name = _('Daily stipend')
+        verbose_name_plural = _('Daily stipends')
+        ordering = ('person', )

### 2016-05-03 scientific_mission/urls.py

@@ -1,0 +1,9 @@
+from django.conf.urls import patterns, url
+from scientific_mission import views
+
+
+urlpatterns = patterns('',
+                       url(r'^load_origin_cities/$', views.load_origin_cities, name='load_origin_cities'),
+                       url(r'^load_destination_cities/$', views.load_destination_cities,
+                           name='load_destination_cities'),
+                       )

### 2016-05-03 scientific_mission/views.py

@@ -1,0 +1,35 @@
+import json as simplejson
+from cities_light.models import Country, City
+from django.contrib.auth.decorators import login_required
+from django.http import HttpResponse
+from django.shortcuts import get_object_or_404
+
+
+def select_cities(country_field):
+    select = City.objects.filter(country_id=country_field)
+    countries = []
+    for country in select:
+        countries.append({'pk': country.id, 'name': country.__unicode__()})
+
+    json = simplejson.dumps(countries)
+    return json
+
+
+@login_required
+def load_origin_cities(request):
+    if request.method == 'GET':
+        origin_country_id = request.GET.get('origin_country')
+        origin_country = get_object_or_404(Country, id=origin_country_id)
+        result = select_cities(origin_country)
+
+        return HttpResponse(result, content_type="application/json")
+
+
+@login_required
+def load_destination_cities(request):
+    if request.method == 'GET':
+        destination_country_id = request.GET.get('destination_country')
+        destination_country = get_object_or_404(Country, id=destination_country_id)
+        result = select_cities(destination_country)
+
+        return HttpResponse(result, content_type="application/json")

### 2016-05-03 sistema/settings.py

@@ -46,6 +46,7 @@ INSTALLED_APPS = (
     'django.contrib.staticfiles',
     'cep',
     'django_jenkins',
+    'cities_light',
 )
 
 # Possible tasks for Jenkins
@@ -64,6 +65,7 @@ PROJECT_APPS = (
     'activity',
     'dissemination',
     'research',
+    'scientific_mission',
 )
 
 
@@ -108,6 +110,8 @@ LANGUAGES = (
     ('pt-br', u'Português'),
     ('en', u'English'),
 )
+
+CITIES_LIGHT_TRANSLATION_LANGUAGES = ['en', 'pt', 'abbr']
 
 LOCALE_PATHS = [os.path.join(BASE_DIR, 'locale')]
 

### 2016-05-03 sistema/urls.py

@@ -21,6 +21,7 @@ urlpatterns = patterns(
     url(r'^research/', include('research.urls')),
     url(r'^person/', include('person.urls')),
     url(r'^dissemination/', include('dissemination.urls')),
+    url(r'^scientific_mission/', include('scientific_mission.urls')),
 ) + static(settings.MEDIA_URL, document_root=settings.MEDIA_ROOT)
 
 admin.site.site_header = _('NeuroMat Individual Report of Activities')

### 2016-05-03 static/js/load_cities.js

@@ -1,0 +1,48 @@
+function load_origin_cities(id_origin_country)
+{
+    var $id_origin_city = $('#id_origin_city');
+
+    $id_origin_city.html('<option value="">Loading...</option>');
+    $.ajax({
+       type: "GET",
+       url: "/scientific_mission/load_origin_cities",
+       dataType: "json",
+       data: {'origin_country':id_origin_country},
+       success: function(result) {
+           $id_origin_city.empty();
+           $id_origin_city.append('<option value="">--------</option>');
+
+           $.each(result, function(i, item){
+               $id_origin_city.append('<option value="'+item.pk+'">'+item.name+'</option>');
+           });
+       },
+       error: function() {
+           alert('Error: No request return.');
+       }
+    });
+}
+
+
+function load_destination_cities(id_destination_country)
+{
+    var $id_destination_city = $('#id_destination_city');
+
+    $id_destination_city.html('<option value="">Loading...</option>');
+    $.ajax({
+       type: "GET",
+       url: "/scientific_mission/load_destination_cities",
+       dataType: "json",
+       data: {'destination_country':id_destination_country},
+       success: function(result) {
+           $id_destination_city.empty();
+           $id_destination_city.append('<option value="">--------</option>');
+
+           $.each(result, function(i, item){
+               $id_destination_city.append('<option value="'+item.pk+'">'+item.name+'</option>');
+           });
+       },
+       error: function() {
+           alert('Error: No request return.');
+       }
+    });
+}

### 2016-05-05 scientific_mission/admin.py
Changed the field that deals with the amount paid to a person

@@ -8,8 +8,8 @@ admin.site.register(Type)
 
 class ScientificMissionAdmin(admin.ModelAdmin):
     fields = ['person', 'mission', 'project_activity', 'origin_country', 'origin_city', 'destination_country',
-              'destination_city', 'departure', 'arrival', 'value']
-    list_display = ('id', 'person', 'mission', 'destination_city', 'departure', 'arrival', 'value')
+              'destination_city', 'departure', 'arrival', 'amount_paid']
+    list_display = ('id', 'value', 'person', 'mission', 'destination_city', 'departure', 'arrival')
     list_display_links = ('id',)
     form = ScientificMissionForm
 admin.site.register(ScientificMission, ScientificMissionAdmin)

### 2016-05-05 scientific_mission/forms.py

@@ -17,6 +17,7 @@ class ScientificMissionForm(forms.ModelForm):
 
     class Meta:
         model = ScientificMission
+        localized_fields = ('amount_paid',)
 
     class Media:
         js = ('/static/js/load_cities.js',)

### 2016-05-05 scientific_mission/migrations/0001_initial.py

@@ -19,7 +19,7 @@ class Migration(migrations.Migration):
                 ('id', models.AutoField(verbose_name='ID', serialize=False, auto_created=True, primary_key=True)),
                 ('departure', models.DateTimeField(verbose_name='Departure')),
                 ('arrival', models.DateTimeField(verbose_name='Arrival')),
-                ('value', models.CharField(max_length=50, null=True, verbose_name='Value', blank=True)),
+                ('amount_paid', models.DecimalField(verbose_name='Amount paid', max_digits=10, decimal_places=2)),
                 ('destination_city', models.ForeignKey(related_name='destination_city', verbose_name='City of destination', to='cities_light.City')),
                 ('destination_country', models.ForeignKey(related_name='destination_country', verbose_name='Country of destination', to='cities_light.Country')),
             ],

### 2016-05-05 scientific_mission/models.py

@@ -38,7 +38,7 @@ class ScientificMission(models.Model):
     destination_city = models.ForeignKey(City, verbose_name=_('City of destination'), related_name='destination_city')
     departure = models.DateTimeField(_('Departure'))
     arrival = models.DateTimeField(_('Arrival'))
-    value = models.CharField(_('Value'), max_length=50, blank=True, null=True)
+    amount_paid = models.DecimalField(_('Amount paid'), max_digits=10, decimal_places=2)
 
     def __unicode__(self):
         return u'%s' % self.person
@@ -47,3 +47,7 @@ class ScientificMission(models.Model):
         verbose_name = _('Daily stipend')
         verbose_name_plural = _('Daily stipends')
         ordering = ('person', )
+
+    def value(self):
+        return "R$ %s" % self.amount_paid
+

### 2016-05-05 sistema/settings.py

@@ -123,6 +123,9 @@ USE_L10N = True
 
 USE_TZ = True
 
+DECIMAL_SEPARATOR = ','
+
+USE_THOUSAND_SEPARATOR = True
 
 # Static files (CSS, JavaScript, Images)
 # https://docs.djangoproject.com/en/1.7/howto/static-files/

### 2016-05-05 templates/report/dissemination/tex/disseminations.tex

@@
-{% autoescape off %}
-{% block content %}
-
-{% if type == 'i' %}
-    \begin{longtable}{ |p{4cm}|p{4cm}|p{5cm}|p{2cm}| }
-    Title & Topics & URL & Date \\
+{% autoescape off %}{% block content %}{% if type == 'i' %}\begin{longtable}{ |p{4cm}|p{4cm}|p{5cm}|p{2cm}| }
 \hline
-    {% for dissemination in disseminations %}
-        {{ dissemination.title }} & {{ dissemination.topics }} & {{ dissemination.link }} & {{ dissemination.date|date:"M d, Y" }} \\
-    \hline
-    {% endfor %}
+Title & Topics & URL & Date \\ \hline
+{% for dissemination in disseminations %}{{ dissemination.title }} & {{ dissemination.topics }} & {{ dissemination.link }} & {{ dissemination.date|date:"M d, Y" }} \\ \hline {% endfor %}
 \end{longtable}
-
 {% elif type == 'e' %}
@@
 \hline
-    \textbf{Title} & \textbf{Authors} & Media outlet & Topics & URL & Date \\
-    \hline
-    {% for dissemination in disseminations %}
-        {{ dissemination.title }} & {{ dissemination.external.authors }} & {{ dissemination.external.media_outlet }} & {{ dissemination.topics }} & {{ dissemination.link }}&#125; & {{ dissemination.date|date:"M d, Y" }} \\
-    \hline
-    {% endfor %}
+Title & Authors & Media outlet & Topics & URL & Date \\ \hline
+{% for dissemination in disseminations %}{{ dissemination.title }} & {{ dissemination.external.authors }} & {{ dissemination.external.media_outlet }} & {{ dissemination.topics }} & {{ dissemination.link }} & {{ dissemination.date|date:"M d, Y" }} \\ \hline {% endfor %}
 \end{longtable}
 {% endif %}
-
 {% endblock %}

### 2016-05-05 scientific_mission/models.py
Unicode def changed

@@ -41,7 +41,7 @@ class ScientificMission(models.Model):
     amount_paid = models.DecimalField(_('Amount paid'), max_digits=10, decimal_places=2)
 
     def __unicode__(self):
-        return u'%s' % self.person
+        return u'%s - %s' % (self.person, self.amount_paid)
 
     class Meta:
         verbose_name = _('Daily stipend')

### 2016-05-05 scientific_mission/models.py
Unicode def changed

@@ -41,7 +41,7 @@ class ScientificMission(models.Model):
     amount_paid = models.DecimalField(_('Amount paid'), max_digits=10, decimal_places=2)
 
     def __unicode__(self):
-        return u'%s - %s' % (self.person, self.amount_paid)
+        return u'%s - R$ %s' % (self.person, self.amount_paid)
 
     class Meta:
         verbose_name = _('Daily stipend')

### 2016-05-05 scientific_mission/admin.py
Changed the order of the fields

@@ -7,8 +7,8 @@ admin.site.register(Type)
 
 
 class ScientificMissionAdmin(admin.ModelAdmin):
-    fields = ['person', 'mission', 'project_activity', 'origin_country', 'origin_city', 'destination_country',
-              'destination_city', 'departure', 'arrival', 'amount_paid']
+    fields = ['person', 'amount_paid', 'mission', 'project_activity', 'origin_country', 'origin_city',
+              'destination_country', 'destination_city', 'departure', 'arrival']
     list_display = ('id', 'value', 'person', 'mission', 'destination_city', 'departure', 'arrival')
     list_display_links = ('id',)
     form = ScientificMissionForm

### 2016-05-06 scientific_mission/models.py
Ordering changed

@@ -46,7 +46,7 @@ class ScientificMission(models.Model):
     class Meta:
         verbose_name = _('Daily stipend')
         verbose_name_plural = _('Daily stipends')
-        ordering = ('person', )
+        ordering = ('-departure', )
 
     def value(self):
         return "R$ %s" % self.amount_paid

### 2016-05-06 scientific_mission/urls.py
NIRA-94 - Create report of Scientific Mission (html and latex)

@@ -6,4 +6,5 @@ urlpatterns = patterns('',
                        url(r'^load_origin_cities/$', views.load_origin_cities, name='load_origin_cities'),
                        url(r'^load_destination_cities/$', views.load_destination_cities,
                            name='load_destination_cities'),
+                       url(r'^report/$', views.missions_report, name='missions_report'),
                        )

### 2016-05-06 scientific_mission/views.py

@@ -1,8 +1,11 @@
 import json as simplejson
 from cities_light.models import Country, City
+from helper_functions.date import *
+from scientific_mission.models import ScientificMission
+from django.contrib import messages
 from django.contrib.auth.decorators import login_required
 from django.http import HttpResponse
-from django.shortcuts import get_object_or_404
+from django.shortcuts import render, get_object_or_404
 
 
 def select_cities(country_field):
@@ -33,3 +36,32 @@ def load_destination_cities(request):
         result = select_cities(destination_country)
 
         return HttpResponse(result, content_type="application/json")
+
+
+@login_required
+def missions_report(request):
+
+    if request.method == 'POST':
+        start_date = request.POST['start_date']
+        if start_date:
+            start_date = start_date_typed(start_date)
+        else:
+            start_date = datetime.datetime.strptime('19700101 00:00:00', '%Y%m%d %H:%M:%S').date()
+
+        end_date = request.POST['end_date']
+        if end_date:
+            end_date = end_date_typed(end_date)
+        else:
+            end_date = now_plus_thirty()
+
+        missions = ScientificMission.objects.filter(departure__gt=start_date,
+                                                    arrival__lt=end_date).order_by('departure')
+
+        if end_date >= start_date:
+            context = {'missions': missions}
+            return render(request, 'report/scientific_mission/scientific_missions_report.html', context)
+        else:
+            messages.error(request, 'End date should be equal or greater than start date.')
+            return render(request, 'report/scientific_mission/scientific_missions.html')
+
+    return render(request, 'report/scientific_mission/scientific_missions.html')

### 2016-05-06 scientific_mission/views.py
NIRA-94 - Create report of Scientific Mission (html and latex)

@@ -55,7 +55,7 @@ def missions_report(request):
             end_date = now_plus_thirty()
 
         missions = ScientificMission.objects.filter(departure__gt=start_date,
-                                                    arrival__lt=end_date).order_by('departure')
+                                                    arrival__lt=end_date).order_by('-departure')
 
         if end_date >= start_date:
             context = {'missions': missions}

### 2016-05-06 dissemination/views.py
NIRA-93 - Generate latex for the dissemination report Generating latex article with name correspondent to internal or external.

@@ -87,6 +87,7 @@ def dissemination_tex(request):
     end_date = request.GET.get('end_date')
     media_type = request.GET.get('type')
     internal_type = request.GET.get('internal_type')
+    filename = request.GET.get('filename')
 
     if media_type == 'i':
         disseminations = internal_filter(internal_type, start_date, end_date)
@@ -98,6 +99,6 @@ def dissemination_tex(request):
 
     response = HttpResponse(render_to_string('report/dissemination/tex/disseminations.tex', context),
                             content_type='text/plain')
-    response['Content-Disposition'] = 'attachment; filename="disseminations.tex"'
+    response['Content-Disposition'] = 'attachment; filename="%s.tex"' % filename
 
     return response

### 2016-05-06 templates/report/scientific_mission/tex/scientific_missions.tex
NIRA-95 - Create latex report Latex report for scientific missions.

{% autoescape off %}{% block content %}\begin{longtable}{ |p{4cm}|p{5,4cm}|p{2cm}|p{1,8cm}|p{1,8cm}| }
\hline
Researcher & Scientific mission & Local & Start date & End date \\ \hline
{% for mission in missions %}{% if mission.person and mission.person.institution == None %}{{ mission.person }}{% elif mission.person and mission.person.institution != None %}{{ mission.person }} / {{ mission.person.institution.get_person_institution }}{% endif %} &{% if mission.mission != None and mission.project_activity != None %}{{ mission.mission }}{{ mission.project_activity.title }}{% elif mission.mission != None %}{{ mission.mission }}{% elif mission.project_activity != None %}{{ mission.project_activity.title }}{% else %}No scientific missions found!{% endif %} &{{ mission.destination_city }} &  {{ mission.departure|date:"M d, Y" }} & {{ mission.arrival|date:"M d, Y" }}\\ \hline {% endfor %}
\end{longtable}

{% endblock %}
{% endautoescape %}

### 2016-05-06 dissemination/views.py

@@ -81,6 +81,7 @@ def dissemination_report(request):
     return render(request, 'report/dissemination/dissemination.html', context)
 
 
+@login_required
 def dissemination_tex(request):
 
     start_date = request.GET.get('start_date')

### 2016-05-06 scientific_mission/urls.py

@@ -7,4 +7,5 @@ urlpatterns = patterns('',
                        url(r'^load_destination_cities/$', views.load_destination_cities,
                            name='load_destination_cities'),
                        url(r'^report/$', views.missions_report, name='missions_report'),
+                       url(r'^scientific_missions_tex/$', views.missions_tex, name='scientific_missions_tex'),
                        )

### 2016-05-06 scientific_mission/views.py

@@ -6,6 +6,7 @@ from django.contrib import messages
 from django.contrib.auth.decorators import login_required
 from django.http import HttpResponse
 from django.shortcuts import render, get_object_or_404
+from django.template.loader import render_to_string
 
 
 def select_cities(country_field):
@@ -42,6 +43,7 @@ def load_destination_cities(request):
 def missions_report(request):
 
     if request.method == 'POST':
+
         start_date = request.POST['start_date']
         if start_date:
             start_date = start_date_typed(start_date)
@@ -58,10 +60,28 @@ def missions_report(request):
                                                     arrival__lt=end_date).order_by('-departure')
 
         if end_date >= start_date:
-            context = {'missions': missions}
+            context = {'start_date': start_date, 'end_date': end_date, 'missions': missions}
             return render(request, 'report/scientific_mission/scientific_missions_report.html', context)
         else:
             messages.error(request, 'End date should be equal or greater than start date.')
             return render(request, 'report/scientific_mission/scientific_missions.html')
 
     return render(request, 'report/scientific_mission/scientific_missions.html')
+
+
+@login_required
+def missions_tex(request):
+
+    start_date = request.GET.get('start_date')
+    end_date = request.GET.get('end_date')
+
+    missions = ScientificMission.objects.filter(departure__gt=start_date,
+                                                arrival__lt=end_date).order_by('-departure')
+
+    context = {'missions': missions}
+
+    response = HttpResponse(render_to_string('report/scientific_mission/tex/scientific_missions.tex', context),
+                            content_type='text/plain')
+    response['Content-Disposition'] = 'attachment; filename="scientific_missions.tex"'
+
+    return response

### 2016-05-06 templates/report/activity/tex/training_programs.tex
NIRA-96 - Create latex reports for the Activity app Created latex reports for seminars and training programs.

{% autoescape off %}{% block content %}\begin{longtable}{ |p{5,5cm}|p{5cm}|p{2cm}|p{1,5cm}| }
\hline
Title & Speaker & Date & Duration \\ \hline
{% for training in training_programs %}{{ training.trainingprogram.title }} & {{ training.trainingprogram.speakers }} & {% if training.trainingprogram.end_date %}{{ training.trainingprogram.start_date|date:"M d, Y" }} - {{ training.trainingprogram.end_date|date:"M d, Y" }} & {% else %}{{ training.trainingprogram.start_date|date:"M d, Y" }} & {% endif %}{% if training.trainingprogram.duration == 'Other' %}{{ training.trainingprogram.other_duration }}  \\ \hline {% else %}{{ training.trainingprogram.duration }}  \\ \hline {% endif %}{% endfor %}
\end{longtable}{% endblock %}{% endautoescape %}

### 2016-05-06 activity/urls.py

@@ -8,4 +8,6 @@ urlpatterns = patterns('',
     url(r'^meetings/$', views.meetings_report, name='meetings_report'),
     url(r'^seminar_poster/$', views.seminar_poster, name='seminar_poster'),
     url(r'^seminar_show_titles/$', views.seminar_show_titles, name='seminar_show_titles'),
+    url(r'^seminar_latex/$', views.seminar_latex, name='seminar_latex'),
+    url(r'^training_programs_latex/$', views.training_programs_latex, name='training_programs_latex'),
 )

### 2016-05-06 activity/views.py

@@ -13,7 +13,7 @@ from django.contrib.auth.decorators import login_required
 from django.http import Http404, HttpResponse
 from django.shortcuts import render, get_object_or_404
 from django.template import Context
-from django.template.loader import get_template
+from django.template.loader import get_template, render_to_string
 from django.utils.translation import ugettext_lazy as _
 
 
@@ -62,7 +62,7 @@ def seminars_report(request):
                                                         seminar__date__lt=end_date).order_by('-seminar__date')
 
         if end_date >= start_date:
-            context = {'seminars': seminars, 'category': category}
+            context = {'start_date': start_date, 'end_date': end_date, 'seminars': seminars, 'category': category}
             return render(request, 'report/activity/seminars_report.html', context)
         else:
             messages.error(request, _('End date should be equal or greater than start date.'))
@@ -71,6 +71,25 @@ def seminars_report(request):
     context = {'categories': categories}
 
     return render(request, 'report/activity/seminars.html', context)
+
+
+@login_required
+def seminar_latex(request):
+
+    start_date = request.GET.get('start_date')
+    end_date = request.GET.get('end_date')
+
+    seminars = ProjectActivities.objects.filter(type_of_activity='s',
+                                                seminar__date__gt=start_date,
+                                                seminar__date__lt=end_date).order_by('-seminar__date')
+
+    context = {'seminars': seminars}
+
+    response = HttpResponse(render_to_string('report/activity/tex/seminars.tex', context),
+                            content_type='text/plain')
+    response['Content-Disposition'] = 'attachment; filename="seminars.tex"'
+
+    return response
 
 
 @login_required
@@ -140,13 +159,33 @@ def training_programs_report(request):
                                                              trainingprogram__start_date__lt=end_date).order_by('trainingprogram__start_date')
 
         if end_date >= start_date:
-            context = {'training_programs': training_programs}
+            context = {'start_date': start_date, 'end_date': end_date, 'training_programs': training_programs}
             return render(request, 'report/activity/training_programs_report.html', context)
         else:
             messages.error(request, _('End date should be equal or greater than start date.'))
             return render(request, 'report/activity/training_programs.html')
 
     return render(request, 'report/activity/training_programs.html')
+
+
+@login_required
+def training_programs_latex(request):
+
+    start_date = request.GET.get('start_date')
+    end_date = request.GET.get('end_date')
+
+    tp = ProjectActivities.objects.filter(type_of_activity='t',
[…]

### 2016-05-06 sistema/settings.py

@@ -52,10 +52,10 @@ INSTALLED_APPS = (
 # Possible tasks for Jenkins
 
 JENKINS_TASKS = (
-    'django_jenkins.tasks.run_pep8',
-    'django_jenkins.tasks.run_pyflakes',
-    'django_jenkins.tasks.run_sloccount',
-    'django_jenkins.tasks.run_pylint',
+    # 'django_jenkins.tasks.run_pep8',
+    # 'django_jenkins.tasks.run_pyflakes',
+    # 'django_jenkins.tasks.run_sloccount',
+    # 'django_jenkins.tasks.run_pylint',
 )
 
 PROJECT_APPS = (

### 2016-05-06 sistema/settings.py
NIRA-96 - Create latex reports for the Activity app Created latex reports for seminars and training programs.

@@ -52,10 +52,10 @@ INSTALLED_APPS = (
 # Possible tasks for Jenkins
 
 JENKINS_TASKS = (
-    # 'django_jenkins.tasks.run_pep8',
-    # 'django_jenkins.tasks.run_pyflakes',
-    # 'django_jenkins.tasks.run_sloccount',
-    # 'django_jenkins.tasks.run_pylint',
+    'django_jenkins.tasks.run_pep8',
+    'django_jenkins.tasks.run_pyflakes',
+    'django_jenkins.tasks.run_sloccount',
+    'django_jenkins.tasks.run_pylint',
 )
 
 PROJECT_APPS = (

### 2016-06-21 templates/report/research/tex/articles.tex
Default

@@
 {% if published_scientific or accepted_scientific or submitted_scientific or draft_scientific or published_dissemin or accepted_dissemin or submitted_dissemin or draft_dissemin or published_tec_trans or accepted_tec_trans or submitted_tec_trans or draft_tec_trans or published_scientific_in_event or accepted_scientific_in_event or published_dissemin_in_event or accepted_dissemin_in_event or published_tec_trans_in_event or accepted_tec_trans_in_event%}
+\begin{enumerate}
 	{% if published_scientific or accepted_scientific %}
 \paragraph{Published or Accepted}
-\begin{enumerate}
 		{% if published_scientific %}

### 2016-06-21 research/views.py

@@ -8,7 +8,7 @@ from random import randint
 from bs4 import BeautifulSoup
 from research.models import *
 from person.models import CitationName
-from helper_functions.latex import tex_escape
+from helper_functions.latex import escape_and_generate_latex
 from helper_functions.date import *
 from django.contrib.auth.decorators import login_required
 from django.contrib import messages
@@ -157,12 +157,14 @@ def articles_tex(request):
                'published_tec_trans_in_event': published_tec_trans_in_event,
                'accepted_tec_trans_in_event': accepted_tec_trans_in_event}
 
-    response = render_to_string('report/research/tex/articles.tex', context)
-    response = tex_escape(response)
-    latex_response = HttpResponse(response, content_type='text/plain')
-    latex_response['Content-Disposition'] = 'attachment; filename="articles.tex"'
+    return escape_and_generate_latex('report/research/tex/articles.tex', context, 'Articles', table=False)
 
-    return latex_response
+    # response = render_to_string('report/research/tex/articles.tex', context)
+    # response = tex_escape(response, table=False)
+    # latex_response = HttpResponse(response, content_type='text/plain')
+    # latex_response['Content-Disposition'] = 'attachment; filename="articles.tex"'
+    #
+    # return latex_response
 
 
 def search_academic_works(start_date, end_date):

### 2016-06-21 templates/report/dissemination/tex/disseminations.tex
NIRA-96 - Create latex reports for the Activity app Created latex reports for seminars and training programs.
NIRA-105 - Delete the author column of the newsletter report

@@
-{% autoescape off %}{% block content %}{% if type == 'i' %}\begin{longtable}{ |p{4cm}|p{4cm}|p{5cm}|p{2cm}| }
+{% autoescape off %}{% block content %}
+{% if type == 'i' and media != "Newsletter" %}\begin{longtable}{ |p{3,5cm}|p{2cm}|p{2,5cm}|p{5cm}|p{2cm}| }
+\hline
+Title & Authors & Topics & URL & Date \\ \hline
+{% for dissemination in disseminations %}{{ dissemination.title }} & {{ dissemination.authors }} & {{ dissemination.topics }} & \url{ {{ dissemination.link }} } & {{ dissemination.date|date:"M d, Y" }} \\ \hline {% endfor %}
+\end{longtable}
+{% elif type == 'i' and media == "Newsletter" %}\begin{longtable}{ |p{4cm}|p{4cm}|p{5cm}|p{2cm}| }
 \hline
 Title & Topics & URL & Date \\ \hline
-{% for dissemination in disseminations %}{{ dissemination.title }} & {{ dissemination.topics }} & {{ dissemination.link }} & {{ dissemination.date|date:"M d, Y" }} \\ \hline {% endfor %}
+{% for dissemination in disseminations %}{{ dissemination.title }} & {{ dissemination.topics }} & \url{ {{ dissemination.link }} } & {{ dissemination.date|date:"M d, Y" }} \\ \hline {% endfor %}
 \end{longtable}
@@
 Title & Authors & Media outlet & Topics & URL & Date \\ \hline
-{% for dissemination in disseminations %}{{ dissemination.title }} & {{ dissemination.external.authors }} & {{ dissemination.external.media_outlet }} & {{ dissemination.topics }} & {{ dissemination.link }} & {{ dissemination.date|date:"M d, Y" }} \\ \hline {% endfor %}
+{% for dissemination in disseminations %}{{ dissemination.title }} & {{ dissemination.external.authors }} & {{ dissemination.external.media_outlet }} & {{ dissemination.topics }} & \url{ {{ dissemination.link }} } & {{ dissemination.date|date:"M d, Y" }} \\ \hline {% endfor %}
 \end{longtable}
-{% endif %}
-{% endblock %}
-{% endautoescape %}
+{% endif %}{% endblock %}{% endautoescape %}

### 2016-06-21 dissemination/views.py

@@ -1,6 +1,6 @@
 # -*- coding: utf-8 -*-
 from helper_functions.date import *
-from helper_functions.latex import generate_latex
+from helper_functions.latex import escape_and_generate_latex
 from dissemination.models import Dissemination, Internal, InternalMediaOutlet, TYPE_OF_MEDIA
 from django.contrib import messages
 from django.contrib.auth.decorators import login_required
@@ -92,10 +92,12 @@ def dissemination_tex(request):
 
     if media_type == 'i':
         disseminations = internal_filter(internal_type, start_date, end_date)
+        internal_media = InternalMediaOutlet.objects.get(pk=internal_type)
+        media = internal_media.name
+        context = {'disseminations': disseminations, 'type': media_type, 'media': media}
 
     else:
         disseminations = external_filter(start_date, end_date)
+        context = {'disseminations': disseminations, 'type': media_type}
 
-    context = {'disseminations': disseminations, 'type': media_type}
-
-    return generate_latex('report/dissemination/tex/disseminations.tex', context, filename)
+    return escape_and_generate_latex('report/dissemination/tex/disseminations.tex', context, filename, table=True)

### 2016-06-21 helper_functions/latex.py

@@ -4,7 +4,7 @@ from django.http import HttpResponse
 from django.template.loader import render_to_string
 
 
-def tex_escape(response):
+def tex_escape(response, table):
     """
         :param: a plain text message
         :return: the message escaped to appear correctly in LaTeX
@@ -12,7 +12,6 @@ def tex_escape(response):
     conv = {
         '{ ': '{',
         ' }': '}',
-        '&': r'\&',
         '%': r'\%',
         '$': r'\$',
         '#': r'\#',
@@ -20,6 +19,11 @@ def tex_escape(response):
         '<': r'\textless',
         '>': r'\textgreater',
     }
+
+    if not table:
+        conv.update({
+            '&': r'\&',
+        })
 
     for key in conv:
         if key in response:
@@ -33,3 +37,12 @@ def generate_latex(tex_view_path, context, filename):
     response = HttpResponse(render_to_string(tex_view_path, context), content_type='text/plain')
     response['Content-Disposition'] = 'attachment; filename="%s.tex"' % filename
     return response
+
+
+# Generate latex file from a view path, with a certain context, with the name desired (using tex_escape!)
+def escape_and_generate_latex(tex_view_path, context, filename, table):
+    response = render_to_string(tex_view_path, context)
+    response = tex_escape(response, table)
+    latex_response = HttpResponse(response, content_type='text/plain')
+    latex_response['Content-Disposition'] = 'attachment; filename="%s.tex"' % filename
+    return latex_response

### 2016-06-21 research/views.py
NIRA-106 - Change the link to the .tex report

@@ -159,13 +159,6 @@ def articles_tex(request):
 
     return escape_and_generate_latex('report/research/tex/articles.tex', context, 'Articles', table=False)
 
-    # response = render_to_string('report/research/tex/articles.tex', context)
-    # response = tex_escape(response, table=False)
-    # latex_response = HttpResponse(response, content_type='text/plain')
-    # latex_response['Content-Disposition'] = 'attachment; filename="articles.tex"'
-    #
-    # return latex_response
-
 
 def search_academic_works(start_date, end_date):
     # Get all the Postdocs among the chosen dates

### 2016-06-21 templates/report/scientific_mission/tex/scientific_missions.tex
NIRA-96 - Create latex reports for the Activity app Created latex reports for seminars and training programs.
Code optimization

@@
 Researcher & Scientific mission & Local & Start date & End date \\ \hline
-{% for mission in missions %}{% if mission.person and mission.person.institution == None %}{{ mission.person }}{% elif mission.person and mission.person.institution != None %}{{ mission.person }} / {{ mission.person.institution.get_person_institution }}{% endif %} &{% if mission.mission != None and mission.project_activity != None %}{{ mission.mission }}{{ mission.project_activity.title }}{% elif mission.mission != None %}{{ mission.mission }}{% elif mission.project_activity != None %}{{ mission.project_activity.title }}{% else %}No scientific missions found!{% endif %} &{{ mission.destination_city }} &  {{ mission.departure|date:"M d, Y" }} & {{ mission.arrival|date:"M d, Y" }}\\ \hline {% endfor %}
-\end{longtable}
-
-{% endblock %}
-{% endautoescape %}
+{% for mission in missions %}{% if mission.person and mission.person.institution == None %}{{ mission.person }}{% elif mission.person and mission.person.institution != None %}{{ mission.person }} / {{ mission.person.institution.get_person_institution }}{% endif %} &{% if mission.mission != None and mission.project_activity != None %}{{ mission.mission }}{{ mission.project_activity.title }}{% elif mission.mission != None %}{{ mission.mission }}{% elif mission.project_activity != None %}{{ mission.project_activity.title }}{% else %}No scientific missions found!{% endif %} & {% if mission.destination_city.country.name == 'Brazil' %}{{ mission.destination_city.name }} - {{ mission.destination_city.region.alternate_names }}{% else %}{{ mission.destination_city.name }}, {{ mission.destination_city.country }}{% endif %} &  {{ mission.departure|date:"M d, Y" }} & {{ mission.arrival|date:"M d, Y" }}\\ \hline {% endfor %}
+\end{longtable}{% endblock %}{% endautoescape %}

### 2016-06-24 templates/report/scientific_mission/tex/scientific_missions.tex
NIRA-107 - Change scientific mission to register multiple routes

--- 2016-05-06 templates/report/scientific_mission/tex/scientific_missions.tex
@@
 Researcher & Scientific mission & Local & Start date & End date \\ \hline
-{% for mission in missions %}{% if mission.person and mission.person.institution == None %}{{ mission.person }}{% elif mission.person and mission.person.institution != None %}{{ mission.person }} / {{ mission.person.institution.get_person_institution }}{% endif %} &{% if mission.mission != None and mission.project_activity != None %}{{ mission.mission }}{{ mission.project_activity.title }}{% elif mission.mission != None %}{{ mission.mission }}{% elif mission.project_activity != None %}{{ mission.project_activity.title }}{% else %}No scientific missions found!{% endif %} &{{ mission.destination_city }} &  {{ mission.departure|date:"M d, Y" }} & {{ mission.arrival|date:"M d, Y" }}\\ \hline {% endfor %}
-\end{longtable}
-
-{% endblock %}
-{% endautoescape %}
+{% for item in missions %}{% if item.mission.person and item.mission.person.institution == None %}{{ item.mission.person }}{% elif item.mission.person and item.mission.person.institution != None %}{{ item.mission.person }} / {{ item.mission.person.institution.get_person_institution }}{% endif %} & {% if item.mission.mission != None and item.mission.project_activity != None %}{{ item.mission.mission }}{{ item.mission.project_activity.title }}{% elif item.mission.mission != None %}{{ item.mission.mission }}{% elif item.mission.project_activity != None %}{{ item.mission.project_activity.title }}{% else %}No scientific missions found!{% endif %} & {% if item.mission.destination_city.country.name == 'Brazil' %}{{ item.mission.destination_city.name }} - {{ item.mission.destination_city.region.alternate_names }}{% else %}{{ item.mission.destination_city.name }}, {{ item.mission.destination_city.country }}{% endif %} &  {{ item.departure.departure|date:"M d, Y" }} & {{ item.arrival.departure|date:"M d, Y" }}\\ \hline {% endfor %}
+\end{longtable}{% endblock %}{% endautoescape %}

### 2016-06-24 scientific_mission/admin.py

@@ -1,15 +1,43 @@
 from scientific_mission.models import *
 from scientific_mission.forms import *
+from suit.admin import SortableTabularInline
 from django.contrib import admin
+from django.core.exceptions import ValidationError
+from django.forms import BaseInlineFormSet
+from django.utils.translation import ugettext_lazy as _
 
 
 admin.site.register(Type)
 
 
+class InlineValidationDate(BaseInlineFormSet):
+    def clean(self):
+        super(InlineValidationDate, self).clean()
+
+        if any(self.errors):
+            return
+
+        for form in self.forms:
+            start_date = form.cleaned_data.pop('departure', None)
+            end_date = form.cleaned_data.pop('arrival', None)
+
+            if start_date and end_date and start_date > end_date:
+                raise ValidationError(_("The arrival date can not be earlier than the departure date."))
+
+
+class RouteInline(SortableTabularInline):
+    model = Route
+    sortable = 'order'
+    extra = 1
+    form = RouteForm
+    formset = InlineValidationDate
+
+
 class ScientificMissionAdmin(admin.ModelAdmin):
-    fields = ['person', 'amount_paid', 'mission', 'project_activity', 'origin_city', 'destination_city', 'departure',
-              'arrival']
-    list_display = ('id', 'value', 'person', 'mission', 'destination_city', 'departure', 'arrival')
+    fields = ['person', 'amount_paid', 'mission', 'project_activity', 'destination_city']
+    list_display = ('id', 'person', 'value', 'mission', 'destination_city')
     list_display_links = ('id',)
+    search_fields = ['person__full_name', 'mission__mission', 'project_activity__title']
+    inlines = (RouteInline,)
     form = ScientificMissionForm
 admin.site.register(ScientificMission, ScientificMissionAdmin)

### 2016-06-24 scientific_mission/forms.py

@@ -1,18 +1,33 @@
-from cities_light.models import City
 from dal import autocomplete
-from scientific_mission.models import ScientificMission
+from scientific_mission.models import ScientificMission, Route
+from suit.widgets import SuitSplitDateTimeWidget
 from django import forms
-from django.utils.translation import ugettext_lazy as _
+
+
+class RouteForm(forms.ModelForm):
+
+    class Meta:
+        model = Route
+        fields = ('origin_city', 'destination_city', 'departure', 'arrival', 'order')
+        widgets = {
+            'origin_city': autocomplete.ModelSelect2(url='city_autocomplete'),
+            'destination_city': autocomplete.ModelSelect2(url='city_autocomplete'),
+            'departure': SuitSplitDateTimeWidget,
+            'arrival': SuitSplitDateTimeWidget
+        }
+
+    class Media:
+        css = {
+            'all': ('/static/css/inline_autocomplete.css',)
+        }
 
 
 class ScientificMissionForm(forms.ModelForm):
 
-    origin_city = forms.ModelChoiceField(queryset=City.objects.all(), label=_('City of origin'), initial=1383,
-                                         widget=autocomplete.ModelSelect2(url='city_autocomplete'))
-    destination_city = forms.ModelChoiceField(queryset=City.objects.all(), label=_('City of destination'), initial=1383,
-                                              widget=autocomplete.ModelSelect2(url='city_autocomplete'))
-
     class Meta:
         model = ScientificMission
         fields = '__all__'
+        widgets = {
+            'destination_city': autocomplete.ModelSelect2(url='city_autocomplete'),
+        }
         localized_fields = ('amount_paid',)

### 2016-06-24 scientific_mission/migrations/0002_add_route.py

@@ -1,0 +1,70 @@
+# -*- coding: utf-8 -*-
+# Generated by Django 1.9.6 on 2016-06-22 21:17
+from __future__ import unicode_literals
+
+from django.db import migrations, models
+import django.db.models.deletion
+
+
+class Migration(migrations.Migration):
+
+    dependencies = [
+        ('cities_light', '0006_compensate_for_0003_bytestring_bug'),
+        ('scientific_mission', '0001_initial'),
+    ]
+
+    operations = [
+        migrations.CreateModel(
+            name='Route',
+            fields=[
+                ('id', models.AutoField(auto_created=True, primary_key=True, serialize=False, verbose_name='ID')),
+                ('departure', models.DateTimeField(verbose_name='Departure')),
+                ('arrival', models.DateTimeField(verbose_name='Arrival')),
+                ('order', models.PositiveIntegerField(verbose_name='Order')),
+                ('destination_city', models.ForeignKey(on_delete=django.db.models.deletion.CASCADE,
+                                                       related_name='destination', to='cities_light.City',
+                                                       verbose_name='To')),
+                ('origin_city', models.ForeignKey(on_delete=django.db.models.deletion.CASCADE, related_name='origin',
+                                                  to='cities_light.City', verbose_name='From')),
+            ],
+        ),
+        migrations.AlterModelOptions(
+            name='scientificmission',
+            options={'ordering': ('-date_of_registration',), 'verbose_name': 'Daily stipend',
+                     'verbose_name_plural': 'Daily stipends'},
+        ),
+        migrations.AddField(
+            model_name='scientificmission',
+            name='date_of_registration',
+            field=models.DateTimeField(auto_now_add=True, null=True, verbose_name='Date'),
+        ),
+        migrations.AddField(
+            model_name='route',
+            name='scientific_mission',
+            field=models.ForeignKey(on_delete=django.db.models.deletion.CASCADE,
+                                    to='scientific_mission.ScientificMission'),
+        ),
+        migrations.AlterField(
+            model_name='scientificmission',
+            name='arrival',
+            field=models.DateTimeField(null=True, verbose_name='Arrival'),
+        ),
+        migrations.AlterField(
+            model_name='scientificmission',
+            name='departure',
+            field=models.DateTimeField(null=True, verbose_name='Departure'),
+        ),
+        migrations.AlterField(
+            model_name='scientificmission',
+            name='destination_city',
+            field=models.ForeignKey(null=True, on_delete=django.db.models.deletion.CASCADE,
[…]

### 2016-06-24 scientific_mission/migrations/0003_copy_data_to_route.py

@@ -1,0 +1,64 @@
+# -*- coding: utf-8 -*-
+# Generated by Django 1.9.6 on 2016-06-22 21:18
+from __future__ import unicode_literals
+from django.db import migrations
+
+
+def reverse_data(apps, schema_editor):
+    model_scientific_mission = apps.get_model("scientific_mission", "ScientificMission")
+    model_route = apps.get_model("scientific_mission", "Route")
+
+    scientific_mission_id = None
+    for route in model_route.objects.all().order_by('scientific_mission_id', 'order'):
+        if route.scientific_mission_id != scientific_mission_id:
+            scientific_mission = model_scientific_mission.objects.get(pk=route.scientific_mission.id)
+            scientific_mission.origin_city_id = route.origin_city.id
+            scientific_mission.destination_city_id = route.destination_city.id
+            scientific_mission.departure = route.departure
+            scientific_mission.save()
+            scientific_mission_id = route.scientific_mission_id
+        else:
+            scientific_mission = model_scientific_mission.objects.get(pk=route.scientific_mission.id)
+            scientific_mission.arrival = route.departure
+            scientific_mission.save()
+
+    model_route.objects.all().delete()
+
+
+def load_data(apps, schema_editor):
+    model_scientific_mission = apps.get_model("scientific_mission", "ScientificMission")
+    model_route = apps.get_model("scientific_mission", "Route")
+
+    for mission in model_scientific_mission.objects.all():
+
+        model_route.objects.create(
+            scientific_mission=mission,
+            origin_city=mission.origin_city,
+            destination_city=mission.destination_city,
+            order=0,
+            departure=mission.departure,
+            arrival=mission.departure
+        )
+
+        model_route.objects.create(
+            scientific_mission=mission,
+            origin_city=mission.destination_city,
+            destination_city=mission.origin_city,
+            order=1,
+            departure=mission.arrival,
+            arrival=mission.arrival
+        )
+
+        mission.date_of_registration = mission.arrival
+        mission.save()
+
+
+class Migration(migrations.Migration):
+
+    dependencies = [
+        ('scientific_mission', '0002_add_route'),
+    ]
+
+    operations = [
+        migrations.RunPython(load_data, reverse_data)
+    ]

### 2016-06-24 scientific_mission/migrations/0004_remove_fields_from_scientific_mission.py

@@ -1,0 +1,27 @@
+# -*- coding: utf-8 -*-
+# Generated by Django 1.9.6 on 2016-06-23 20:32
+from __future__ import unicode_literals
+
+from django.db import migrations
+
+
+class Migration(migrations.Migration):
+
+    dependencies = [
+        ('scientific_mission', '0003_copy_data_to_route'),
+    ]
+
+    operations = [
+        migrations.RemoveField(
+            model_name='scientificmission',
+            name='arrival',
+        ),
+        migrations.RemoveField(
+            model_name='scientificmission',
+            name='departure',
+        ),
+        migrations.RemoveField(
+            model_name='scientificmission',
+            name='origin_city',
+        ),
+    ]

### 2016-06-24 scientific_mission/models.py

@@ -31,11 +31,9 @@ class ScientificMission(models.Model):
     person = models.ForeignKey(Person, verbose_name=_('Paid to'))
     mission = models.ForeignKey(Type, verbose_name=_('Mission'), blank=True, null=True)
     project_activity = models.ForeignKey(ProjectActivities, verbose_name=_('Project activity'), blank=True, null=True)
-    origin_city = models.ForeignKey(City, verbose_name=_('City of origin'))
-    destination_city = models.ForeignKey(City, verbose_name=_('City of destination'), related_name='destination_city')
-    departure = models.DateTimeField(_('Departure'))
-    arrival = models.DateTimeField(_('Arrival'))
+    destination_city = models.ForeignKey(City, verbose_name=_('City of destination'))
     amount_paid = models.DecimalField(_('Amount paid'), max_digits=10, decimal_places=2)
+    date_of_registration = models.DateTimeField(_('Date'), auto_now_add=True, null=True)
 
     def __unicode__(self):
         return u'%s - R$ %s' % (self.person, self.amount_paid)
@@ -43,7 +41,16 @@ class ScientificMission(models.Model):
     class Meta:
         verbose_name = _('Daily stipend')
         verbose_name_plural = _('Daily stipends')
-        ordering = ('-departure', )
+        ordering = ('-date_of_registration',)
 
     def value(self):
         return "R$ %s" % self.amount_paid
+
+
+class Route(models.Model):
+    scientific_mission = models.ForeignKey(ScientificMission)
+    origin_city = models.ForeignKey(City, related_name='origin', verbose_name=_('From'))
+    destination_city = models.ForeignKey(City, related_name='destination', verbose_name=_('To'))
+    departure = models.DateTimeField(_('Departure'))
+    arrival = models.DateTimeField(_('Arrival'))
+    order = models.PositiveIntegerField(_('Order'))

### 2016-06-24 scientific_mission/tests.py

@@ -2,16 +2,20 @@ import datetime
 from django.core.urlresolvers import reverse
 from django.test import TestCase
 from cities_light.models import City, Country
-from scientific_mission.models import ScientificMission
+from scientific_mission.models import ScientificMission, Route
 from person.models import Person
 from research.tests import system_authentication
 
 
 # Create a scientific mission for testing
-def scientific_mission(person, city, departure, arrival, amount_paid):
-    return ScientificMission(person=person,
-                             origin_city=city, destination_city=city,
-                             departure=departure, arrival=arrival, amount_paid=amount_paid)
+def scientific_mission(person, amount_paid):
+    return ScientificMission(person=person, amount_paid=amount_paid)
+
+
+# Create routes
+def create_route(city, mission, date_time, order):
+    return Route(scientific_mission=mission, origin_city=city, destination_city=city, departure=date_time,
+                 arrival=date_time, order=order)
 
 
 class ScientificMissionsTest(TestCase):
@@ -38,19 +42,29 @@ class ScientificMissionsTest(TestCase):
         person = Person(full_name="Fulano Testeiro")
         person.save()
 
-        departure1 = datetime.date(2015, 1, 15)
-        arrival1 = datetime.date(2015, 1, 16)
+        date_departure1 = datetime.date(2015, 1, 15)
+        date_arrival1 = datetime.date(2015, 1, 16)
 
-        departure2 = datetime.date(2014, 1, 15)
-        arrival2 = datetime.date(2014, 1, 16)
+        date_departure2 = datetime.date(2014, 1, 15)
+        date_arrival2 = datetime.date(2014, 1, 16)
+        order_01 = 0
+        order_02 = 1
 
         amount_paid = 666
 
-        mission1 = scientific_mission(person, city, departure1, arrival1, amount_paid)
+        mission1 = scientific_mission(person, amount_paid)
         mission1.save()
+        route1_mission1 = create_route(city, mission1, date_departure1, order_01)
+        route2_mission1 = create_route(city, mission1, date_arrival1, order_02)
+        route1_mission1.save()
+        route2_mission1.save()
 
-        mission2 = scientific_mission(person, city, departure2, arrival2, amount_paid)
+        mission2 = scientific_mission(person, amount_paid)
         mission2.save()
+        route1_mission2 = create_route(city, mission2, date_departure2, order_01)
+        route2_mission2 = create_route(city, mission2, date_arrival2, order_02)
+        route1_mission2.save()
+        route2_mission2.save()
 
     def test_report(self):
 
[…]

### 2016-06-24 scientific_mission/views.py

@@ -11,7 +11,7 @@ from helper_functions.date import *
 from helper_functions.latex import generate_latex
 from helper_functions.extenso import dExtenso
 from person.models import Person
-from scientific_mission.models import ScientificMission
+from scientific_mission.models import ScientificMission, Route
 
 
 class CityAutocomplete(autocomplete.Select2QuerySetView):
@@ -73,7 +73,7 @@ def anexo5(request):
 
             ext = dExtenso()
             amount = str(int(mission.amount_paid))
-            cents = str(mission.amount_paid - int(mission.amount_paid))[2:4] # Apenas dois digitos nos centavos
+            cents = str(mission.amount_paid - int(mission.amount_paid))[2:4]  # Apenas dois digitos nos centavos
             amount = ext.getExtenso(amount)
             cents = ext.getExtenso(cents)
 
@@ -112,6 +112,21 @@ def mission_show_titles(request):
         return HttpResponse(json, content_type="application/json")
 
 
+def get_missions(start_date, end_date):
+    missions = []
+    for mission in ScientificMission.objects.all():
+        routes = Route.objects.filter(scientific_mission=mission).order_by('order')
+        if routes:
+            departure = routes.first()
+            arrival = routes.last()
+
+            if departure.departure.date() >= start_date and arrival.departure.date() <= end_date:
+                valid_mission = {'mission': mission, 'departure': departure, 'arrival': arrival}
+                missions.append(valid_mission)
+
+    return missions
+
+
 @login_required
 def missions_report(request):
 
@@ -129,10 +144,8 @@ def missions_report(request):
         else:
             end_date = now_plus_thirty()
 
-        missions = ScientificMission.objects.filter(departure__gt=start_date,
-                                                    arrival__lt=end_date).order_by('-departure')
-
         if end_date >= start_date:
+            missions = get_missions(start_date, end_date)
             context = {'start_date': start_date, 'end_date': end_date, 'missions': missions}
             return render(request, 'report/scientific_mission/scientific_missions_report.html', context)
         else:
@@ -148,8 +161,8 @@ def missions_tex(request):
     start_date = request.GET.get('start_date')
     end_date = request.GET.get('end_date')
 
-    missions = ScientificMission.objects.filter(departure__gt=start_date,
-                                                arrival__lt=end_date).order_by('-departure')
+    missions = get_missions(datetime.datetime.strptime(start_date, "%Y-%m-%d").date(),
[…]

### 2019-11-29 templates/report/dissemination/tex/disseminations.tex
Changing the way of the report tables that have title and url and the last breaks the table

--- 2016-05-05 templates/report/dissemination/tex/disseminations.tex
@@
-{% autoescape off %}{% block content %}{% if type == 'i' %}\begin{longtable}{ |p{4cm}|p{4cm}|p{5cm}|p{2cm}| }
+{% autoescape off %}{% block content %}
+{% if type == 'i' and media != "Newsletter" %}\begin{longtable}{ |p{5cm}|p{3cm}|p{4cm}|p{3cm}| }
+\hline
+Title & Authors & Topics & Date \\ \hline
+{% for dissemination in disseminations %}\href{ {{ dissemination.link }} }{\texttt{ {{ dissemination.title }} }} & {{
+dissemination.authors }} & {{ dissemination.topics }} & {{ dissemination.date|date:"M d, Y" }} \\ \hline {% endfor %}
+\end{longtable}
+{% elif type == 'i' and media == "Newsletter" %}\begin{longtable}{ |p{7cm}|p{5cm}|p{3cm}| }
 \hline
 Title & Topics & URL & Date \\ \hline
-{% for dissemination in disseminations %}{{ dissemination.title }} & {{ dissemination.topics }} & {{ dissemination.link }} & {{ dissemination.date|date:"M d, Y" }} \\ \hline {% endfor %}
+{% for dissemination in disseminations %}\href{ {{ dissemination.link }} }{\texttt{ {{ dissemination.title }} }} & {{
+dissemination.topics }} & {{ dissemination.date|date:"M d, Y" }} \\ \hline {% endfor %}
 \end{longtable}
 {% elif type == 'e' %}
-\begin{longtable}{ |p{3cm}|p{2,3cm}|p{2cm}|p{3cm}|p{3,5cm}|p{1,2cm}| }
+\begin{longtable}{ |p{5cm}|p{3cm}|p{2cm}|p{3cm}|p{2cm}| }
 \hline
-Title & Authors & Media outlet & Topics & URL & Date \\ \hline
-{% for dissemination in disseminations %}{{ dissemination.title }} & {{ dissemination.external.authors }} & {{ dissemination.external.media_outlet }} & {{ dissemination.topics }} & {{ dissemination.link }} & {{ dissemination.date|date:"M d, Y" }} \\ \hline {% endfor %}
+Title & Authors & Media outlet & Topics & Date \\ \hline
+{% for dissemination in disseminations %}\href{ {{ dissemination.link }} }{\texttt{ {{ dissemination.title }} }} & {{
+dissemination.external.authors }} & {{ dissemination.external.media_outlet }} & {{ dissemination.topics }} & {{ dissemination.date|date:"M d, Y" }} \\ \hline {% endfor %}
 \end{longtable}
-{% endif %}
-{% endblock %}
-{% endautoescape %}
+{% endif %}{% endblock %}{% endautoescape %}
